### 2017-07-29 Tex_Dissertation/MSc_dissertation.tex
moving all

\documentclass[12pt,a4paper]{report}

\usepackage{graphics}
%\usepackage{fullpage,epsf,graphicx, amstext,url} 
%\usepackage{epsf}
\usepackage{graphicx}
\usepackage{amstext}
\usepackage{url}
\usepackage{amssymb}
\usepackage{graphicx}
%\graphicspath{ {/home/george/Desktop/Tex_Dissertation/images} }
%
% head.sty is no longer needed
%
%\usepackage{head,fullpage,epsf,graphicx, amstext,url}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\thispagestyle{empty}

%                       This is a basic LaTeX Template
%                       for the MSc Dissertation report
%
\parindent=10pt          %  Switch off indent of paragraphs 
\parskip=5pt            %  Put 5pt between each paragraph  
%
%                       This section generates a title page
%                       Edit only the sections indicated to put
%                       in the project title, and submission date
%

\vspace*{0.1\textheight}

\begin{center}
        \huge{\bfseries Calculation of the Supersymmetric top quark mass at CLIC}\\
\end{center}

\bigskip

\begin{center}
        \large{Georgios Billis}\\      % Replace with your name
        \bigskip
        \large{August 18, 2017}        % Submission Date
\end{center}

%%% If necessary, reduce the number 0.4 below so the University Crest
%%% and the words below it fit on the page.
%%% Don't let the crest and the wording below it flow onto the next page!
\vspace*{0.35\textheight}

\begin{center}
        \includegraphics[width=35mm]{crest.pdf}
\end{center}

\medskip

\begin{center}

%%%
%%% Change Theoretical to Mathematical if appropriate
%%%
\large{
  MSc in Theoretical Physics\\[0.8ex]
  The University of Edinburgh\\[0.8ex]
  2017
}

\end{center}

\newpage

\pagenumbering{roman}

\begin{abstract}
In this project I calculate the mass of the Supersymmetric top quark in CLIC experiment at $\sqrt{s}$ = 3 TeV in $e^{-}$ $e^{+}$ collisions. I assume the following decay for the top squark $\tilde{q} \rightarrow q$ $\chi_{0}$, 
and I focus on the fully hadronic channel of decay i.e $\tilde{q} \rightarrow q$ $\chi_{0} \rightarrow$ $W b \tilde{\chi}_{1}^{0}$ .
The mass was found  to be  $m_{\tilde{t}}$ = 861 $\pm$ 19 GeV using the Boosted Descision 
Trees Multivariate Analysis and $m_{\tilde{t}}$ = 812 $\pm$ 20 GeV using the Gradient Boosted Descision  Trees Multivariate Analysis. 
\end{abstract}

\pagenumbering{roman}

\textbf{Declaration}

\newpage

\tableofcontents
\listoftables
\listoffigures

\begin{titlepage}
\vspace*{2in}
% an acknowledgements section is completely optional but if you decide
% not to include it you should still include an empty {titlepage}
% environment as this initialises things like section and page numbering.
\section*{Acknowledgements}

Put your acknowledgements here. Thanking your supervisor for his/her
help is standard practice, but you don't have to do this\ldots

This template is is modification of the one for the MSc in High
Performance Computing, which is apparently descended from a template
developed by Prof Charles Duncan for MSc students in Meteorology. His
acknowledgement follows:

\emph{This template has been produced with help from many former
  students who have shown different ways of doing things. Please make
  suggestions for further improvements.}

Some parts of this template were lifted unashamedly from the Edinburgh
MPhys project report guide, with little or no modification. I have no
idea who wrote the first version of that\ldots

You don't have to use \LaTeX\ for your dissertation. You can use
Microsoft Word or Apple Pages if you wish, but it's \emph{much} easier
to typeset equations in \LaTeX, and references look after
themselves. Whatever you use, your dissertation should have the same
general structure, and it should look similar to this one --
especially the front page.

\end{titlepage}

\pagenumbering{arabic}

\chapter{Introduction}

On July 2012 the discovery of the Higgs boson was announced at CERN's Large Hadron Collider (LHC). This marked the begining of a new era for experimental High Energy Physics motivating the design of new 
experiments for further and deeper exploration of the Higgs boson itsel but also, addressing the questions/problems that arose with it.

One of these experiments is Compact Linear Collider (CLIC), a high-luminosity linear $e^{-}$ $e^{+}$ collider. It is designed for a staging scenario of three main centre of mass energies at $\surd{s}$ = 380 GeV, $\surd{s}$ = 1.5 TeV
and $\surd{s}$ = 3 TeV targeting optimal physics output based on the current landscape. The main difference of CLIC with LHC is that in the latter, protons collide which are non fundamental particles as they consist of quarks and 
gluons bound alltogether. One of the disadvantages of LHC is the inability to know beforehand the initial state of the colliding particles as quarks exist in a "sea of gluons" making it impossible to know their momenta. This sets
some restrictions with resprect to the precision that it can probe various observables.

On the other hand, CLIC is designed to invastigate the interactions of elementary particles, an important advantage since initial states of the colliding particles is known. In advance, LHC suffers from energy loss due to 
Synchrotron radiation since protons are accelerated in a 27 km circular accelerator whereas CLIC, being linear does not.

The main targets of CLIC are dependent of the energy stage. In the first it will focus on prescision standard model physics such as Higgs and Top quark measurements and in the two subsequent, among others, there will be searches
for new physics~\cite{clic2016updated}. One of the theories that aspires to give solutions to many of the problems of Standard Model is Supersymmetry (SUSY). In this theory every particle has a Supersymmetric partner that differs in the spin by $1/2$, thus 
relating bosons with fermions and fermios with bosons.

In the Minimal Supersymmetric Standard Model, the top squarks $\tilde{t}$ decay almost all the times into a top quark $t$
and a dark matter candidate, the neutralino $\tilde{\chi}_{1}^{0}$. In this project I will use Multivariate Analisis
to discriminate the best it can be achieved between signal and background with the goal to measure the top squark
mass at $\surd{s}$ = 3 TeV in the CLIC accelerator environment.

\chapter{CLIC}

\section{Outline of the experiment}

CLIC is a proposed $e^{-}$ $e^{+}$ linear collider optimised to perform in three centre of mass stages at 
$\surd s$ = 380 GeV, $\surd s$ = 1.5 TeV and $\surd s$ = 3 TeV. The purpose of the different energy stages is to 
fully exploit its scientific potential including precision measurements and searches for physics Beyond the 
Standar Model.

Specifically, at $\surd s$ = 380 GeV and with an integrated luminosity of $\mathcal{L}_{int}$ = 500 fb$^{-1}$, 
prescision measurements can be made in the Higgs and the top quark sector. At this enegy stage the Higgsstrahlung
process ($e^{+}e^{-}\rightarrow ZH$) alongside the $WW$ fusion ($e^{+}e^{-}\rightarrow H\nu_{e}\tilde{\nu}_{e}$) 
are the dominant and can shed light to properties of the Higgs boson in a model independent way~\cite{clic2016updated}.
Furthermore at the next two stages leading role will play the propsed scenarios for physics BSM with most 
importantly Supersymmetry at $\surd s$ = 3 TeV and with $\mathcal{L}_{int}$ = 2000 fb$^{-1}$. This  is because CLIC has the potential for direct particle detection up to the 
kinematic limit of $\surd s /2$ but also through indirect detection of observables that are sensitive to BSM
scenarios exploiting the full energy potential.

Given the linear nature of CLIC, there are no energy losses induced by Synchrotron radiation which appears in 
circular colliders, but due Beamsstrahlung radiation. As the colsliding bunches get closer to the 
vertex, the strong electromagnetic fields (up to 10 Tesla) created by the opposing beam cause deflection
of the partices trajectories resulting to emit Synchrotron radiation. The effect is energy-dependent with huge
impact at higher energies~\cite{bonvicini1989first} as it can be seen in the following image~\cite{abramowicz2017higgs}.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.7\linewidth]{{images/beamsstrahlung}.png}
  \caption{The luminosity spectrum for CLIC operating at $\surd s$ = 3 TeV, where $\surd s'$ is the
  effective centre-of-mass energy after beamstrahlung and initial state radiation }
  \label{fig2.15}
\end{figure}

\chapter{Supersymmetry}

\section{}

This section should be written in standard scientific
language. Standard techniques in your research field should not be
written out in detail. In computational projects this section should
be used to explain the algorithms used and the layout of the
computational code. A copy of the actual code may be given in the
appendices if appropriate.

This section should emphasise the philosophy of the approach used and
detail novel techniques. However please note: this section should not
be a blow-by-blow account of what you did throughout the project. It
should not contain large detailed sections about things you tried and
found to be completely wrong! However, if you find that a technique
that was expected to work failed, that is a valid result and should be
included.

Here logical structure is particularly important, and you may find
that to maintain good structure you may have to present the
explorations/calculations/computations/whatever in a different order
from the one in which you carried them out.

You might sometimes want to include multiple equations in one place
\begin{eqnarray}
  E &=& ma^{2} \\
  E &=& mb^{2} \\
  E &=& mc^{2}
\end{eqnarray}
You might want to include multiple equations in one place without
numbering them
\begin{eqnarray*}
  E &=& ma^{2} \\
  E &=& mb^{2} \\
  E &=& mc^{2}
\end{eqnarray*}
You might want to include multiple equations in one place without
numbering \emph{all} of them
\begin{eqnarray}
  E &=& ma^{2} \nonumber \\
  E &=& mb^{2} \nonumber \\
  E &=& mc^{2}
\end{eqnarray}

You might also want to include diagrams.  The example shows the use of
the special command which allows existing postscript files to be
included.  You would normally keep your figures separate from the text. 
These pictures might be images or pdf output from some
program.

Below I create a figure which is centred and stretched to 30\% of the
width of the page \verb+{0.30\hsize}+ and with the height stretched by
the same amount \verb+{!}+ to preserve the aspect ratio. If you omit
the extension (ie .eps, .ps or .pdf) on the file name then \LaTeX\ will
pick up the postscript copy whereas pdflatex will automatically pick
up the PDF version.

\begin{figure}

\begin{center}
  \resizebox{0.30\hsize}{!}{\includegraphics{crest.pdf}}
\end{center}

\caption{The University Crest}
\label{fig:eucrest}

\end{figure}

You should find the file crest.pdf on this wiki.

% note that labels do not need to include a description of the object
% they are labelling but it can be helpful, eg \label{fig:figurename}.

You can use a label on a figure to refer to it later. The university
crest is in Figure~(\ref{fig:eucrest}). Note that you should not use
phrases like ``the figure above'' or ``the following figure'' since
\LaTeX\ may move the figure relative to the text if it cannot be fitted
onto the current page.

\chapter{Another Chapter Title}
\section{Number of Chapters}

You may vary the number of chapters. The Introduction and Background
Theory chapter are essential, although you may choose a different
title for the latter. These two introductory chapters are usually
followed by a chapter on what you did yourself, with a title such as
Design and Development, although you can choose any title you
wish. After that, you might to have another chapter, or you may go
straight to the Results and Conclusions chapter.

After the Introduction, you are free to use any chapter titles you wish.

\chapter{Results and Analysis}

This section should detail the obtained results in a clear,
easy-to-follow manner. It is important to make clear what are original
results and what are repeats of previous calculations or computations.
Remember that long tables of numbers are just as boring to read as
they are to type-in!

Use graphs to present your results wherever practicable.

Results or computations should be presented with uncertainties
(errors), both statistical and systematic where applicable.

Be selective in what you include: half a dozen \emph{e.g.}~tables that
contain wrong data you collected while you forgot to switch on the
computer are not relevant and may mask the correct results.

\section{Some results}
Here are some results.

\subsection{More results}
When showing results you are likely to use tables and graphs. You can
create tables easily in \LaTeX.

\begin{table}[h]
\begin{center}
\begin{tabular}{||l|c|l||}
\hline
\textbf{File names} & \textbf{Satellite} & \textbf{Resolution}\\
\hline
  worldr            &  Meteosat          &   5km\\
  worldg            &  Meteosat          &   5km\\
  worldb            &  Meteosat          &   5km\\
\hline
\end{tabular}
\end{center}
\caption{This is a simple table. More complicated tables can have
headings which pass over more than one column}
\label{simple_table}
\end{table}

If you want to produce fancier tables than shown in Table \ref{simple_table}
refer to the \LaTeX\ manual or ask Google.

One of the simplest ways to produce simple graphs is to use gnuplot
which produces \LaTeX\  output. Graph~(\ref{fig:gnu}) was produced using
gnuplot with output designated as \LaTeX\  so that a \LaTeX\  output file is
produced which you can include directly or keep separate and refer to
using the \emph{include} command.

Another approach is to draw simple figures using \emph{xfig} which allows
you to export diagrams in \LaTeX\  picture format so that the diagram can
be included directly.

Perhaps the most robust way to include graphs is to convert them to
PostScript or PDF and include them in the same was as was done in
Figure~\ref{fig:eucrest} for the University Crest. You can usually do
this with most packages, including Microsoft ones; one trick for
producing PostScript is to print to a dummy PostScript printer.

% in practice you would probably keep this in a separate file and use
% the \include{filename} command to insert it here.

\begin{figure}
% GNUPLOT: LaTeX picture
\setlength{\unitlength}{0.240900pt}
\ifx\plotpoint\undefined\newsavebox{\plotpoint}\fi
\sbox{\plotpoint}{\rule[-0.200pt]{0.400pt}{0.400pt}}%
\begin{picture}(1500,1200)(0,0)
\font\gnuplot=cmr10 at 10pt
\gnuplot
\sbox{\plotpoint}{\rule[-0.200pt]{0.400pt}{0.400pt}}%
\put(220.0,113.0){\rule[-0.200pt]{292.934pt}{0.400pt}}
\put(220.0,113.0){\rule[-0.200pt]{0.400pt}{245.477pt}}
\put(220.0,113.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(198,113){\makebox(0,0)[r]{$0$}}
\put(1416.0,113.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(220.0,317.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(198,317){\makebox(0,0)[r]{$0.2$}}
\put(1416.0,317.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(220.0,521.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(198,521){\makebox(0,0)[r]{$0.4$}}
\put(1416.0,521.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(220.0,724.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(198,724){\makebox(0,0)[r]{$0.6$}}
\put(1416.0,724.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(220.0,928.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(198,928){\makebox(0,0)[r]{$0.8$}}
\put(1416.0,928.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(220.0,1132.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(198,1132){\makebox(0,0)[r]{$1$}}
\put(1416.0,1132.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(220.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(220,68){\makebox(0,0){$0$}}
\put(220.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(414.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(414,68){\makebox(0,0){$1$}}
\put(414.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(607.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(607,68){\makebox(0,0){$2$}}
\put(607.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(801.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(801,68){\makebox(0,0){$3$}}
\put(801.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(995.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(995,68){\makebox(0,0){$4$}}
\put(995.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(1188.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(1188,68){\makebox(0,0){$5$}}
\put(1188.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(1382.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(1382,68){\makebox(0,0){$6$}}
\put(1382.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(220.0,113.0){\rule[-0.200pt]{292.934pt}{0.400pt}}
\put(1436.0,113.0){\rule[-0.200pt]{0.400pt}{245.477pt}}
\put(220.0,1132.0){\rule[-0.200pt]{292.934pt}{0.400pt}}
\put(45,622){\makebox(0,0){\shortstack{This is\\the\\$y$ axis}}}
\put(828,23){\makebox(0,0){This is the $x$ axis}}
\put(828,1177){\makebox(0,0){This is a plot of $y=sin(x)$}}
\put(220.0,113.0){\rule[-0.200pt]{0.400pt}{245.477pt}}
\sbox{\plotpoint}{\rule[-0.500pt]{1.000pt}{1.000pt}}%
\put(1306,1067){\makebox(0,0)[r]{sin(x)}}
\multiput(1328,1067)(20.756,0.000){4}{\usebox{\plotpoint}}
\put(1394,1067){\usebox{\plotpoint}}
\put(220,113){\usebox{\plotpoint}}
\multiput(220,113)(3.768,20.411){4}{\usebox{\plotpoint}}
\multiput(232,178)(4.132,20.340){3}{\usebox{\plotpoint}}
\multiput(245,242)(3.825,20.400){3}{\usebox{\plotpoint}}
\multiput(257,306)(3.884,20.389){3}{\usebox{\plotpoint}}
\multiput(269,369)(3.944,20.377){3}{\usebox{\plotpoint}}
\multiput(281,431)(4.326,20.300){3}{\usebox{\plotpoint}}
\multiput(294,492)(4.137,20.339){3}{\usebox{\plotpoint}}
\multiput(306,551)(4.276,20.310){3}{\usebox{\plotpoint}}
\multiput(318,608)(4.693,20.218){3}{\usebox{\plotpoint}}
\multiput(331,664)(4.583,20.243){2}{\usebox{\plotpoint}}
\multiput(343,717)(4.754,20.204){3}{\usebox{\plotpoint}}
\multiput(355,768)(5.034,20.136){2}{\usebox{\plotpoint}}
\multiput(367,816)(5.760,19.940){2}{\usebox{\plotpoint}}
\multiput(380,861)(5.579,19.992){3}{\usebox{\plotpoint}}
\put(398.00,923.50){\usebox{\plotpoint}}
\multiput(404,943)(7.049,19.522){2}{\usebox{\plotpoint}}
\multiput(417,979)(7.288,19.434){2}{\usebox{\plotpoint}}
\put(433.18,1021.10){\usebox{\plotpoint}}
\multiput(441,1040)(8.982,18.712){2}{\usebox{\plotpoint}}
\put(460.41,1076.97){\usebox{\plotpoint}}
\put(471.84,1094.28){\usebox{\plotpoint}}
\put(484.84,1110.41){\usebox{\plotpoint}}
\put(500.42,1124.01){\usebox{\plotpoint}}
\multiput(503,1126)(19.159,7.983){0}{\usebox{\plotpoint}}
\put(519.48,1131.37){\usebox{\plotpoint}}
\multiput(527,1132)(20.136,-5.034){0}{\usebox{\plotpoint}}
\put(539.74,1128.60){\usebox{\plotpoint}}
\put(557.04,1117.38){\usebox{\plotpoint}}
\put(570.79,1101.95){\usebox{\plotpoint}}
\put(582.44,1084.80){\usebox{\plotpoint}}
\put(593.09,1066.99){\usebox{\plotpoint}}
\multiput(601,1053)(8.430,-18.967){2}{\usebox{\plotpoint}}
\put(619.18,1010.54){\usebox{\plotpoint}}
\multiput(625,996)(7.413,-19.387){2}{\usebox{\plotpoint}}
\multiput(638,962)(6.403,-19.743){2}{\usebox{\plotpoint}}
\multiput(650,925)(5.830,-19.920){2}{\usebox{\plotpoint}}
\multiput(662,884)(5.461,-20.024){2}{\usebox{\plotpoint}}
\multiput(674,840)(5.533,-20.004){2}{\usebox{\plotpoint}}
\multiput(687,793)(4.937,-20.160){3}{\usebox{\plotpoint}}
\multiput(699,744)(4.667,-20.224){2}{\usebox{\plotpoint}}
\multiput(711,692)(4.858,-20.179){3}{\usebox{\plotpoint}}
\multiput(724,638)(4.276,-20.310){3}{\usebox{\plotpoint}}
\multiput(736,581)(4.205,-20.325){3}{\usebox{\plotpoint}}
\multiput(748,523)(4.070,-20.352){3}{\usebox{\plotpoint}}
\multiput(760,463)(4.326,-20.300){3}{\usebox{\plotpoint}}
\multiput(773,402)(3.884,-20.389){3}{\usebox{\plotpoint}}
\multiput(785,339)(3.884,-20.389){3}{\usebox{\plotpoint}}
\multiput(797,276)(4.070,-20.352){3}{\usebox{\plotpoint}}
\multiput(810,211)(3.825,-20.400){3}{\usebox{\plotpoint}}
\multiput(822,147)(3.607,-20.440){2}{\usebox{\plotpoint}}
\put(828,113){\usebox{\plotpoint}}
\end{picture}
\caption{Simple Gnuplot example}
\label{fig:gnu}
\end{figure}

\section{Discussion of your results}

This section should give a picture of what you have taken out of your
project and how you can put it into context.

This section should summarise the results obtained, detail conclusions
reached, suggest future work, and changes that you would make if you
repeated the project.

\chapter{Conclusions}

This is the place to put your conclusions about your work. You can
split it into different sections if appropriate. You may want to include
a section of future work which could be carried out to continue your
research.

The conclusion section should be at least one page long, preferably 2
pages, but not much longer.

\appendix
% the appendix command just changes heading styles for appendices.

\chapter{Stuff that's too detailed}

Appendices should contain all the material which is considered too
detailed to be included in the main body of the text, but which is
important enough to be included in the thesis.

Perhaps this is a good place to mention \BibTeX.

You can do references in the simple way explained in the introduction,
or you can use \BibTeX.

\section{\BibTeX}
\label{sec:bibtex}

It is convenient to use \BibTeX\ to compile your bibliography.  First
you need to create a .bib file e.g.  you may call it ref.bib Then you
can put all your references into the file with entries such as
\begin{verbatim}
@Book{ob:bornwolf,
     author = "Born, M and Wolf, E",
     title  = "Principles of Optics",
     publisher = "Cambridge University Press",
     year = 1999,
     edition = {7th},
}

@Article{jr:ashkin,
Author = {A. Ashkin and J.M. Dziedzic and J.E. Bjorkholm and S. Chu},
Title = "Observation of a single beam gradient force optical tap for 
dielectric particles",
Journal = "Optics Letters",
Volume = 11,
Pages = "288-290",
Year = 1986}

@INPROCEEDINGS{seger,
 author = {J. Seger and H.J. Brockman},
 title = {What is bet-hedging?},
 editors={P.H. Harvey and L. Partridge},
 booktitle = {Oxford Surveys in Evolutionary Biology},
 year={1987},
 page={18},
 publisher={Oxford University Press},
 place={Oxford}}
\end{verbatim}
for a book, an article in a journal or an article in a proceedings volume
respectively.

Inside your \LaTeX\ file
you should include 
\begin{verbatim}
\bibliographystyle{unsrt}                      
and
\bibliography{ref}
\end{verbatim}
The first command determines the reference style, here plain and 
unsorted. With this referencing style 
a numerical referencing system (which is now the most
common in physics literature) is used and the numbering of references
will be the order in which they appear in the document. Alternatively, 
you could use
a customised `style file' but there is no real need.  The second
command just inputs your .bib file Note that only the references cited
in the text will appear in the bibliography so you can have spare
references in your .bib file.

You use the name you have given to an entry (e.g.
for the book example above the name is ob:bornwolf)
to cite the relevant article
by using the cite command in your \LaTeX\ file e.g. \cite{ob:bornwolf}

\section{Producing your documents using \texttt{pdflatex}}

To use pdflatex your figures need to be in pdf format.  You can convert almost any image file to pdf using \texttt{convert}.  e.g. \texttt{convert myfigure.png myfigure.pdf}.

The first time you should type:
\begin{verbatim}
  pdflatex ProjectReport
  bibtex ProjectReport
  pdflatex ProjectReport
  pdflatex ProjectReport
\end{verbatim} 
This first time you run\texttt{pdflatex} it will produce a
\texttt{ProjectReport.aux}.  The \BibTeX\ command reads in the
bibliography file and makes the files \texttt{ProjectReport.bbl} and
\texttt{ProjectReport.blg} files.  These files are read in the next
\texttt{pdflatex} command, but you'll still have ``undefined
cross-reference'' errors which are sorted out by the last
\texttt{pdflatex} command.

Subsequently, you should only need to do one (or two)
\texttt{pdflatex}s, or \texttt{pdfbibtex} followed by
\texttt{pdflatex} twice if you change any references.

\vspace{5mm} You may also use plain \texttt{latex} instead of
\texttt{pdflatex}.  This requires you to use postscript graphics
instead of pdf.

\chapter{Stuff that won't be read by anyone}

Some people include in their thesis a lot of detail, particularly lots
of tables containing raw results, figures of intermediate results, or
computer code which no-one will ever read. You should be careful that
anything like this you include should contain some element of
uniqueness which justifies its inclusion.

\newpage

\bibliographystyle{unsrt}
\bibliography{MSc_dissertation}

\end{document}

### 2017-07-30 Tex_Dissertation/MSc_dissertation.tex
new

@@
 This marked the begining of a new era for experimental High Energy Physics motivating the design of new
-experiments for further and deeper exploration of the Higgs boson itsel but also, addressing the questions/problems that arose with it.
+experiments for further and deeper exploration of the Higgs boson itself but also, a huge ma addressing the questions/problems that arose with it.
 
@@
 are the dominant and can shed light to properties of the Higgs boson in a model independent way~\cite{clic2016updated}.
-Furthermore at the next two stages leading role will play the propsed scenarios for physics BSM with most 
+In CLIC there is also a dedicated program for top quark physics, as it is one of the most important particles
+in SM because it couples strongest to the Higgs field due to its mass but also it has an important role in 
+many of the BSM scenarios.
+Furthermore at the next two stages leading role will play the proposed scenarios for physics BSM with most 
 importantly Supersymmetry at $\surd s$ = 3 TeV and with $\mathcal{L}_{int}$ = 2000 fb$^{-1}$. This  is because CLIC has the potential for direct particle detection up to the 
 kinematic limit of $\surd s /2$ but also through indirect detection of observables that are sensitive to BSM
-scenarios exploiting the full energy potential.
+scenarios through precision measurements and comparison with the SM expectations, 
+taking advantage of the full energy potential.
 
@@
 circular colliders, but due Beamsstrahlung radiation. As the colsliding bunches get closer to the 
-vertex, the strong electromagnetic fields (up to 10 Tesla) created by the opposing beam cause deflection
+vertex, the strong electromagnetic fields (up to 10 Tesla) created by the opposing beam, cause deflection
 of the partices trajectories resulting to emit Synchrotron radiation. The effect is energy-dependent with huge
-impact at higher energies~\cite{bonvicini1989first} as it can be seen in the following image~\cite{abramowicz2017higgs}.
+impact at higher energies~\cite{bonvicini1989first} as it can be seen in the following 
+image~\cite{abramowicz2017higgs}.
 
@@
 
+CLIC is designed to operate for seven, five and six years respectively in each energy stage while the 
+upgrading periods will last two years. The total run will last for 22 years with the following table summarising
+the luminosities achieved in each stage:
+
+\begin{table}[h]
+
+\centering % used for centering table
+\begin{tabular}{c c} % centered columns (4 columns)
+\hline %inserts double horizontal lines
+$\surd s$ (GeV)  & $\mathcal{L}$   \\ 
+\hline % inserts single horizontal line
+380 & 500 fb^{-1} &
+1.5 & 1.5 ab^{-1} &
+3   &  2 ab^{-1}
+ &\hline %inserts single line
+\end{tabular}
+\label{table:nonlin} % is used to refer this table in the text
+\end{table}
+
+Furthermore, the experiment has two detector concepts CLIC SiD and CLIC ILD in order to serve the required 
+jet energy resolution. The latter has been  developed for the International Linear Collinder but it has been
+adapted according to the needs of CLIC. Both detectors have strong central solenoid magnets creating an axial 
+magnetic field of 5T for CLIC SiD and 4T for CLI ILD~\cite{abramowicz2017higgs}.
+
 \chapter{Supersymmetry}
 
-\section{}
+\section{Motivation}
 
-This section should be written in standard scientific
-language. Standard techniques in your research field should not be
-written out in detail. In computational projects this section should
-be used to explain the algorithms used and the layout of the
-computational code. A copy of the actual code may be given in the
-appendices if appropriate.
+The model that describes elementary particle physics is the Standar Model. It involves matter  fields (fermions)
+and vector gauge bosons (force carriers) that they stem from the fact that the SM Lagrngian is subject to $SU(3) \otimes 
+SU(2) \otimes U(1)$ symmetries. An important part of this theory is the existence of the Higgs field which appeared
+during the unification of the electromagnetic and the weak force. It is known for the fact that it "gives"
+mass to the elementary particles (besides photons and gluons which they are protected by the $U(1)$,$SU(3)$
+symmetries respectively.
 
-This section should emphasise the philosophy of the approach used and
-detail novel techniques. However please note: this section should not
-be a blow-by-blow account of what you did throughout the project. It
-should not contain large detailed sections about things you tried and
-found to be completely wrong! However, if you find that a technique
-that was expected to work failed, that is a valid result and should be
-included.
+It is true that even with the great success that the SM has been probed does not consist a flawless theory.
+Many parts of it are still to be answered or contain significant controversies. One example is the Hierarchy 
+problem. In the electroweak sector of the SM there is a parameter that has the diminsions of energy, the 
+vacum expectation value of the Higgs field which phenomenologicaly is
 
-Here logical structure is particularly important, and you may find
-that to maintain good structure you may have to present the
-explorations/calculations/computations/whatever in a different order
-from the one in which you carried them out.
+\begin{equation}
+ \upsilon \approx 246 \quad GeV
+\end{equation}
 
-You might sometimes want to include multiple equations in one place
-\begin{eqnarray}
-  E &=& ma^{2} \\
-  E &=& mb^{2} \\
-  E &=& mc^{2}
-\end{eqnarray}
-You might want to include multiple equations in one place without
-numbering them
-\begin{eqnarray*}
-  E &=& ma^{2} \\
-  E &=& mb^{2} \\
-  E &=& mc^{2}
-\end{eqnarray*}
-You might want to include multiple equations in one place without
-numbering \emph{all} of them
-\begin{eqnarray}
-  E &=& ma^{2} \nonumber \\
-  E &=& mb^{2} \nonumber \\
-  E &=& mc^{2}
-\end{eqnarray}
+The importance of this parameter is that it sets the masses of the the theory and as well as the Higgs boson
+itself as it is
 
-You might also want to include diagrams.  The example shows the use of
-the special command which allows existing postscript files to be
-included.  You would normally keep your figures separate from the text. 
-These pictures might be images or pdf output from some
-program.
+\begin{equation}
+ M_{H} = \upsilon \sqrt{\frac{\lambda}{2}} 
+\end{equation}
 
-Below I create a figure which is centred and stretched to 30\% of the
-width of the page \verb+{0.30\hsize}+ and with the height stretched by
-the same amount \verb+{!}+ to preserve the aspect ratio. If you omit
-the extension (ie .eps, .ps or .pdf) on the file name then \LaTeX\ will
-pick up the postscript copy whereas pdflatex will automatically pick
-up the PDF version.
+where $\lambda$ is the constant of the Higgs self interaction. The problem arises when we try compute higher 
+order corrections to the mass of the Higgs field. The self energy of the higgs boson has a term of the form
 
-\begin{figure}
+\begin{equation}
+ \int_{}^{\Lambda} d^{4}k \quad f(k,external\quad momenta)
+\end{equation}
 
-\begin{center}
-  \resizebox{0.30\hsize}{!}{\includegraphics{crest.pdf}}
-\end{center}
+where $\Lambda$ represents the scale of the new physics such as the effects of quantum gravity. In dimensional 
+regularisation, when $\Lambda \rightarrow \infty$ the renormalisability of the theory assures that there
+is no inconsistency, but if we take into account a scale, for example, for the quantum gravity then $\Lambda \rightarrow 
+M_{P} \approx 1.2\times 10^{19}\quad GeV$ which is the Plank mass, then the additive quantum corrections for the Higgs 
+mass become too big dragging the value of the Higgs mass up. Because the VEV of the Higgs boson has a fixed 
+phenomenologicaly value, one way to circumvent this problem is by relating bosons with fermions since in the 
+latter, the algebraic terms for their self energies come with a minus sign giving the desired calcelations 
+without any "fine tuning" from our side. This results into the SUSY theory stabilising the Hierarchy $M_{H}
+\ll M_{P}$ with the constraint that the SUSY particles should be visible at a scale not too much greater 
+than 1-10 TeV~\cite{aitchison2005supersymmetry}.
 
-\caption{The University Crest}
-\label{fig:eucrest}
+\section{SUSY Phenomenology}
 
-\end{figure}
+Inside SUSY every boson has a fermionic supersymmetric partner and every fermion has a bosonic one. The 
+fermion superpartners are called sfermions and differ in the spin value by 1/2 whereas the boson particles 
+which are the force carries are related to a spin 1/2 particles, the gauginos. In the following table I show
+the correspondance between SM and SUSY gauge particles.
 
-You should find the file crest.pdf on this wiki.
+\begin{table}[ht]
 
-% note that labels do not need to include a description of the object
-% they are labelling but it can be helpful, eg \label{fig:figurename}.
+\centering % used for centering table
+\begin{tabular}{c c c c} % centered columns (4 columns)
+\hline\hline %inserts double horizontal lines
+Standard Model  &  & SUSY &  \\ [0.5ex] 
+\hline % inserts single horizontal line
+Photon & \gamma & Photino & \tilde{\gamma} \\ % inserting body of the table
+Gluon & g & Gluino & \tilde{g} \\
+Z Boson & Z & Zino & \tilde{Z} \\
+W Boson & W^{\pm,0} & Wino & \tilde{W}^{\pm,0} \\
+B Boson& B & Bino & \tilde{B} \\ [1ex] % [1ex] adds vertical space
+\hline %inserts single line
+\end{tabular}
+\label{table:nonlin} % is used to refer this table in the text
+\end{table}
 
-You can use a label on a figure to refer to it later. The university
-crest is in Figure~(\ref{fig:eucrest}). Note that you should not use
-phrases like ``the figure above'' or ``the following figure'' since
-\LaTeX\ may move the figure relative to the text if it cannot be fitted
-onto the current page.
+The framework of this project is the Minimal Supersymmetric Standard Model which besides the SM particles 
+includes the sleptons $\tilde{\ell}^{\pm}$, the sneutrinos $\tilde{\nu}_{l}$, the squarks $\tilde{q}$, the 
+gluinos $\tilde{g}$, two pair of charginos $\tilde{\chi}^{\pm}_{i}$ where $i=1,2$, four neutralinos 
+$\tilde{\chi}^{0}_{i}$, $i=1,...,4$ and five Higgs bosons $h^{0}$, $H^{0}$, $A^{0}$,$H^{\pm}$.
 

### 2017-07-31 Tex_Dissertation/MSc_dissertation.tex
nw

@@
 \usepackage{graphicx}
+\usepackage{amsmath}
+
 %\graphicspath{ {/home/george/Desktop/Tex_Dissertation/images} }
@@
 This marked the begining of a new era for experimental High Energy Physics motivating the design of new
-experiments for further and deeper exploration of the Higgs boson itself but also, a huge ma addressing the questions/problems that arose with it.
+experiments for further and deeper exploration of the Higgs boson itself but also, a huge marathon
+addressing the questions/problems that arose with it.
 
-One of these experiments is Compact Linear Collider (CLIC), a high-luminosity linear $e^{-}$ $e^{+}$ collider.
+One of these proposed experiments is Compact Linear Collider (CLIC), a high-luminosity linear $e^{-}$ $e^{+}$ collider.
 It is designed for a staging scenario of three main centre of mass energies at $\surd{s}$ = 380 GeV, $\surd{s}$ = 1.5 TeV
@@
 In this theory every particle has a Supersymmetric partner that differs in the spin by $1/2$, thus
-relating bosons with fermions and fermios with bosons.
+relating bosons with fermions and fermions with bosons.
 
@@
 importantly Supersymmetry at $\surd s$ = 3 TeV and with $\mathcal{L}_{int}$ = 2000 fb$^{-1}$. This  is because CLIC has the potential for direct particle detection up to the 
-kinematic limit of $\surd s /2$ but also through indirect detection of observables that are sensitive to BSM
+kinematic limit of $\surd s /2$ for pair production but also through indirect detection of observables that are sensitive to BSM
 scenarios through precision measurements and comparison with the SM expectations, 
@@
 mass to the elementary particles (besides photons and gluons which they are protected by the $U(1)$,$SU(3)$
-symmetries respectively.
+symmetries respectively)
+via Spontaneous Symmetry Breaking .
 
@@
 Many parts of it are still to be answered or contain significant controversies. One example is the Hierarchy 
-problem. In the electroweak sector of the SM there is a parameter that has the diminsions of energy, the 
+problem. In the electroweak sector of the SM there is a parameter that has the dimensions of energy, the 
 vacum expectation value of the Higgs field which phenomenologicaly is
@@
 
-Inside SUSY every boson has a fermionic supersymmetric partner and every fermion has a bosonic one. The 
+Inside SUSY every boson is related to a fermionic supersymmetric partner and every fermion has a bosonic one. The 
 fermion superpartners are called sfermions and differ in the spin value by 1/2 whereas the boson particles 
@@
 $\tilde{\chi}^{0}_{i}$, $i=1,...,4$ and five Higgs bosons $h^{0}$, $H^{0}$, $A^{0}$,$H^{\pm}$.
+
+Both particles and sparticles belong to the same super-multiplet having the same mass and the same quantum 
+numbers as their SM partners but with different spin. Because no such degenerate fermion-boson pair exists 
+in nature,
+then it is deduced that SUSY must be a broken symmetry. In order to constitute a solid solution to the 
+Hierarchy problem, then the difference in the masses of the particles and their supersymmetric partners 
+must be of the order of $\mathcal{O}(1  TeV) $~\cite{nagashima2014beyond}.
+
+In Standard Model, for the Spontaneous Symmetry Breaking one Higgs doublet is needed with 4 degrees of 
+freedom. For the SUSY model on the other hand two such doublets are required with a total of eight 
+degrees of freedom where three of them are absorbed to give mass to the SM particles such as W$^{\pm}$ and Z,
+and the remaining five give rise to five physical Higgs bosons $\tilde{h}$,$\tilde{H}^{\pm}$,$\tilde{A}$,
+$\tilde{H}^{0}$. Those in turn, mix further to become the neutralinos and the charginos : $\tilde{\chi}_{i}^{0}$,
+$\tilde{\chi}_{i}^{\pm}$.
+
+It is known that within the SM the fermions carry chirality denoted by L or R whether they are left or right 
+respectively, according to the way they transform under the symmetry group $SU(2) \otimes U(1)$. Thus given 
+the SUSY relation of fermions-bosons that means that the sfermions  (bosonic superpartners), come into 
+doublets of the form $(f_{i},\tilde{f}_{i})$, where i=L,R. The sfermions mix further to make the eigenstates
+of the mass matrix. This mixing is expected to be strong for third generation sfermions since the Yukawa 
+couplings can be large, more precisely in our case the stop quark mixing effects can be large because
+of the large mass of the top quark.
+
+The following matrix is the mixing matrix expressed in the $(\tilde{f}_{L},\tilde{f}_{R})$ basis:
+
+\begin{equation}
+ \mathcal{M}^{2}_{\tilde{f}} =
+\[  
+  \begin{pmatrix}
+   M^{2}_{\tilde{f}_{L}}  &  \alpha_{f}m_{f} \\
+   \alpha_{f}m_{f}        &  M^{2}_{\tilde{f}_{R}}
+  \end{pmatrix}
+\]
+\end{equation}
+
+where the $M^{2}_{\tilde{f}_{L}}$ are terms that depend on the mass of the quark, the charge and the third 
+component of the weak isospin. The off diagonal elements $\alpha_{f}$ are dependent on the soft SUSY breaking
+trilinear scalar coupling parameters.
+
+In this project I will focous on the top squarks  where the mixing   $\tilde{t}_{R}-\tilde{t}_{L}$ is important
+due to the large top quark mass. By computing the eigenvalues of the previous matrix and for the right
+flavour we obtain:
+
+\begin{equation}
+ m^{2}_{\tilde{t}_{1,2}} = \frac{1}{2}(M^{2}_{\tilde{t}_{L}} + M^{2}_{\tilde{t}_{R}} \mp 
+ \sqrt{(M^{2}_{\tilde{t}_{L}}-M^{2}_{\tilde{t}_{R}})^{2} + 4 m^{2}_{t}\alpha^{2}_{t}})
+\end{equation}
+
+It is obvious that the $m^{2}_{\tilde{t}_{1}}$ will have the lowest mass, something that makes it the 
+lightest squark.
 

### 2017-08-01 Tex_Dissertation/MSc_dissertation.tex
neww

@@
 \hline %inserts double horizontal lines
-$\surd s$ (GeV)  & $\mathcal{L}$   \\ 
-\hline % inserts single horizontal line
-380 & 500 fb^{-1} &
-1.5 & 1.5 ab^{-1} &
-3   &  2 ab^{-1}
- &\hline %inserts single line
+$\surd s$ (GeV)  & $\mathcal{L}$   \\ \hline % inserts single horizontal line
+380 & 500 fb$^{-1}$  \\
+1.5 & 1.5 ab$^{-1}$ \\
+3   &  2 ab$^{-1}$ 
+ %inserts single line
 \end{tabular}
@@
 
+One other feature that makes SUSY attractive is the fact that it includes the convergence of the couplings,
+something that it is known as Grand Unification. From the point of view of SM, something like that is 
+unable to achieve since two of the couplings decrease with energy (weak and strong coupling) whereas one
+(electromagnetic) increases. In the MSSM, by the inclusion of the sparticles such unification is actually
+achievable as it can be seen in the following figure:
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.7\linewidth]{{images/PWOct14gates-fig2-full}.jpg}
+  \label{}
+\end{figure}
+
 \section{SUSY Phenomenology}
@@
 \hline % inserts single horizontal line
-Photon & \gamma & Photino & \tilde{\gamma} \\ % inserting body of the table
-Gluon & g & Gluino & \tilde{g} \\
-Z Boson & Z & Zino & \tilde{Z} \\
-W Boson & W^{\pm,0} & Wino & \tilde{W}^{\pm,0} \\
-B Boson& B & Bino & \tilde{B} \\ [1ex] % [1ex] adds vertical space
+Photon & $\gamma$ & Photino & $\tilde{\gamma}$ \\ % inserting body of the table
+Gluon & g & Gluino & $\tilde{g}$ \\
+Z Boson & Z & Zino & $\tilde{Z}$ \\
+W Boson & $W^{\pm,0}$ & Wino & $\tilde{W}^{\pm,0}$ \\
+B Boson& B & Bino & $\tilde{B}$ \\ [1ex] % [1ex] adds vertical space
 \hline %inserts single line
@@
 
-\chapter{Another Chapter Title}
-\section{Number of Chapters}
+\section{Results from LHC for SUSY}
 
-You may vary the number of chapters. The Introduction and Background
-Theory chapter are essential, although you may choose a different
-title for the latter. These two introductory chapters are usually
-followed by a chapter on what you did yourself, with a title such as
-Design and Development, although you can choose any title you
-wish. After that, you might to have another chapter, or you may go
-straight to the Results and Conclusions chapter.
+ The search for indications for Supersymmetry is not new as LHC has been optimized and focused among other
+ to the direct or indirect detection of sparticles. The majority of the cases that have been studied, 
+ consider as main decay channel of the sparticles the following:
 
-After the Introduction, you are free to use any chapter titles you wish.
+ \begin{equation}
+  BR(\tilde{q} \rightarrow q  \chi_{i}^{0,\pm}) = 100 \%
+ \end{equation}
+
+So far thought no indication of SUSY has been found in LHC but through each analysis the exclusion limits 
+for the SUSY observables become bigger and bigger as it can be seen in the following figures that summarises
+the latest of them for the stop quark mass at $\surd s$ = 8,13 GeV in proton proton collisions
+~\cite{aaboud2016search}:
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.7\linewidth]{{images/ATLAS_SUSY_Stop_tLSP}.png}
+  \label{fig2.15}
+\end{figure}
+
+Whereas in the following figure there are the exclusion limits in ATLAS for p-p collisions at 13 TeV for the
+channel invastiged in this project
+
+ \begin{figure}[ht!]
+  \centering
+  \includegraphics[width=0.7\linewidth, scale=5]{{images/fig_08}.png}
+  \label{}
+\end{figure}
+
+\chapter{Methods}
+\section{Introduction}
+
+In this chapter I will describe the exact conditions and methods that were followed in this project for the 
+calculation of the stop quark mass at CLIC Conceptual experiment.
+
+I will invedtigate the production of a pair of stop quarks at $\surd s$ = 3 TeV and assumig an  integrated 
+luminosity of $\mathcal{L}_{int}$ = 2000 fb$^{-1}$. The channel of interest is the following:
+
+\begin{equation}
+ e^{+} e^{+} \rightarrow \tilde{t} \tilde{\bar{t}} \rightarrow t\tilde{\chi}_{1}^{0} \bar{t}\tilde{\chi}_{1}^{0}
+ \rightarrow W^{+}W^{-}b\bar{b} \tilde{\chi}_{1}^{0} \tilde{\chi}_{1}^{0}
+\end{equation}
+
+and for this model the mass of the top squark is $m_{\tilde{t}}$ = 844 GeV whereas the mass of the 
+neutralino is $m_{\tilde{\chi}_{1}^{0}}$. This is not the only possible decay of a top squark but it is the
+dominant one. In what follows I show the top three branching ratios of the top squark decay and two
+of the corresponding Feynmann diagrams:
+
+\begin{figure}[ht!]
+  \raggedleft
+  \includegraphics[width=0.4\linewidth]{{images/feyn1}.png}
+  \hspace{\fill}
+    \includegraphics[width=0.4\linewidth]{{images/feyn2}.png}
+  \label{}
+\end{figure}
+
+\newpage
+
+\begin{enumerate}
+ \item BR($\tilde{t}\rightarrow t \tilde{\chi}_{1}^{0}$) = 52.4 \%
+ \item BR($\tilde{t}\rightarrow b \tilde{\chi}_{1}^{\pm}$) = 34.1 \%
+ \item BR($\tilde{t}\rightarrow t \tilde{\chi}_{2}^{0}$) = 13.2 \%
+ \end{enumerate}
+
+As also the branching ratios for the decay of the W boson to either in a hadronic final state or in
+a leptonic one are:
+
+\begin{itemize}
+ \item BR($W\rightarrow q\bar{q}$) = 67.8 \% 
+ \item BR($W\rightarrow l\nu_{l}$) = 32.2 \%
+\end{itemize}
+
+In the following I summarise the possible decays of the stops indicating the branching pair fraction
+for each one:
+
+\begin{itemize}
+ \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t \tilde{\chi}_{1}^{0}
+ \chi^{\pm}_{1}b \rightarrow
+ W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}$ \quad (35.8\%)
+
+ \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t\bar{t} \tilde{\chi}_{1}^{0}
+ \tilde{\chi}^{0}_{1} \rightarrow
+ W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}$ \quad (27.4\%)
+
+ \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t\bar{t} \tilde{\chi}_{1}^{0}
+ \chi^{0}_{2} \rightarrow
+ W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}h$ \quad (13.7\%)
+
+ \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow b\bar{b} \chi_{1}^{+}
+ \chi^{-}_{1} \rightarrow
+ W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}$ \quad (11.6\%)
+
+ \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t \tilde{\chi}_{2}^{0}
+ \chi^{\pm}_{1}b \rightarrow
+ W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}h$ \quad (9\%)
+
+ \end{itemize}
+
+\newpage
+
+\section{Calculation of SUSY particle masses}
 

### 2017-08-03 Tex_Dissertation/MSc_dissertation.tex
n

@@
 
+There are various ways that have been developed for the calculation of the squark masses at electron-positron
+linear colliders. In this chapter I present one that will not be used in my analysis but sketch the potencial
+and thus the importance of the aforementioned colliders regarding these kind of calculations.
+
+The main topologies that are considered are those that the gluino is heavier than the squarks and thus the 
+dominant decaying channel is:
+
+\begin{equation}
+ e^{-}e^{+} \rightarrow \tilde{q} \tilde{\bar{q}} \rightarrow q\bar{q}\chi_{1}^{0}\chi_{1}^{0}
+\end{equation}
+
+It needs to be mentioned that a powerfull advantage of the CLIC experiment is the possibility of achieving 
+polarisation up to 80$\%$ helping to reduce the WW background and the ability to create right or left squarks
+depending on the needs of the physical analysis.
+
+\subsection{Modified Invariant Mass}
+
+This technique has been developed initially for LHC experiment where the p-p collision energy is not known.
+The calculation was achieved by creating the variable $M_{C}$ which is related to the standard 
+invariant mass but it's invariance comes from contra linear boosts of equal magnitude. The squark mass is given
+by:
+
+\begin{equation}
+ m_{\tilde{q}}=\frac{1}{2} \big(M_{C}^{max} + \sqrt{(M_{C}^{max})^{2} + 4m_{\chi}^{2}} \big)
+\end{equation}
+
+where
+
+\begin{equation}
+ M_{C}^{2}=2(E_{q,1}E_{q,2}+\vec{p}_{q,1}\vec{p}_{q,2})
+\end{equation}
+
+and
+
+\begin{equation}
+ M_{C}^{max}=\frac{m^{2}_{\tilde{q}}-m^{2}_{\chi}}{m_{\tilde{q}}}
+\end{equation}
+
+The power off this kind of calculation comes from the fact that no knowledge for the exact center of mass 
+energy is needed (In comparison with the first method described in~\cite{simon2010techniques}), something that is not purely known since the effects of initial state radiation and
+the Beamstrahlung can distort it significantly resulting to even bigger uncertainties. Note that this method 
+assumes that the mass of the neutralino is known and that the quark is massless.
+
+\section{Minimisaton of $\chi^{2}$ Method}
+
+In this chapter I describe the procedure that I followed until the calculation of the top squark mass. 
+This involved the vertex finding, the jet clustering, the flavourtagging and the calculation of the $\chi^{2}$
+for each top squark mass.
+
+\subsection{Vertex Finding}
+
+For the needs of this projecct I used the package of LCFIplus which is an improved software of the already 
+existing one LCFIVertex. The important difference between the  two is that LCFIplus employs the vertex finding 
+befere the jet clustering (in comparison to LCFIVertex which follows the exact oposite procedure) with the 
+goal to protect the secondadry vertices from breaking up and grouped into different jets~\cite{suehara2016lcfiplus}.
+This is an important step towards better performance since the Bottom jets can be identified from their 
+sufficiently large distance between the primary vertex and their decay vertex. Additionally, the importance
+of this step to be performed before jet clustering, is that hadrons that contain bottom or charm quarks 
+have sizeable lifetimes and they can be measured Inside the detector.
+
+That said, the vertex finding was the first step towards obtaining the final data for analysis.
+
+\subsection{Jet Clustering}
+
+Jets are an indespensible part of high energy physics. They come from the manifestation of strong nuclear
+as free quarks or gluons hadronize. They are visual structures that are measured in the detectors and they
+serve the need of approaching the initial parton that they originated. Throught the years various algorithms 
+have been developed for the clustering of such objects differing in the way that the approach suchh procedure.
+Two of the most famous are the sequential recombination algorithms and cone algorithms. In this projecct I use
+the a sequential recombination algorithm, the $k_{t}$ algorithm which is a longitudinaly invariant algorithm
+firstly designed for hadron colliders.
+
+The $k_{t}$ involves a measure of distance $d_{ij}$ for all the pair of particles $i,j$:
+
+\begin{equation}
+ d_{ij}=d_{ji}=min(p_{Ti}^{2},p_{Tj}^{2})\frac{\Delta R^{2}_{ij}}{R^{2}}
+\end{equation}
+
+where $p_{Ti}$ is the transverse momentum of $i^{th}$ particle with respect to beam direction and 
+$\Delta R^{2}_{ij}=(y_{i}-y_{j})^{2}+(\phi_{i}-\phi_{j})^{2}$ with $y$ being the rapitdity, $\phi$ being
+the azimuth angle and R the jet radius fixed in this project as $R=0.7$.
+
+The basic idea behind this algorithm is that it calculates the $d_{ij}$ with the smallest value and then it 
+"merges" the $i,j$ into a single object with momentum $p_{i}+p_{j}$. This procedure is repeated until the quantity
+$d_{ij}$ is above some threshold and all the particles that are left are the event's jet
+~\cite{cacciari2012fastjet}.
+
+\subsection{Flavour Tagging}
+
 \chapter{Results and Analysis}

### 2017-08-04 Tex_Dissertation/MSc_dissertation.tex
no

@@
 
+Flavour Tagging is the procedure in which a pseudoprobability is assigned to each jet regarding the parton
+that the jet originates from. In this project, there are six jets in the final products four of them 
+originating from b quarks.
+
+The flavour tagging algorithm that was used belonged in the LCFIplus package~\cite{suehara2016lcfiplus}.
+It  makes use of the TMVA package which in turn uses multivariate classifiers. A set of input variables are 
+defined for each jet and they are passed to the Gradien Boosted Descision Trees (a certain type of classifiers)
+which they are trained and then applied to the jets of the physical process. Those input variables are
+constituents of the jets such as tracks and secondary vertices.
+
+\subsection{Classification Method: \textit{Boosted Descision Trees}}
+
+For the calculation of the top squark mass I made use of the TMVA package wich is provides a multivariate 
+analysis platform in order (for this project) to make separation between the signal and the background. Two 
+of them were empoyed and used and compaired: the \textit{Boosted Descision Trees} (BDT) and the 
+\textit{Gradient Boosted Descision Trees} (GBDT).
+
+In this chapter I describe the Boosted Descision Trees method of classification and cite the results of this 
+investigation.
+
+\subsubsection{Background on BDT's}
+
+Before I explain what BDT's are, it would be beneficial to sketch what Descision Trees are.
+
+Suppose we start with signal and background events described by a set of variables such as (in HEP) transverse 
+momenta, missing energy, etc. Then we sort all events by each variable and we choose the one that gives the
+best separation between signal and background. This is how the first node is made. Then, in the two branches 
+that are made we repeat this procedure applying the best cut on each node until the splitting stops based on 
+some criterion. That is how the terminal node is reached which is called leaf~\cite{hoecker2007tmva}.
+
+One \textit{issue} that arises for Descision Trees is their instability in statistical fluctuations. If two 
+of the input variables have similar separation power then a fluctuation of the input sample may cause the 
+selection of one of the two variables disregarding the other, something that would not happen if the fluctuation
+was not present. This results in a totaly different tree structure.
+
+A way to circumvent this problem is to employ many different trees whose depth is small. They are called
+weak learners. The classification of the event comes from the majority vote of these weak learners (boosting).
+It is important to be noted that each tree is trainned with the same sample of input variables. That way not 
+only we reach better results in the possible presence of statistical fluctuations but we also avoid the 
+overtrainning of the trees.
+
+\subsubsection{Separation of Signal and Background}
+
+In the physical case that I examine I have what will later be denoted as SUSY signal: corresponding to the 
+top squarks, SUSY and SM background: corresponding to any physical process that immitates the one under 
+consideration.
+
+To this end, using the TMVA package in root and trainning 200 trees with the  preselection cuts:
+
+\begin{itemize}
+ \item $E_{visible} <$ 2 TeV
+ \item $E_{top 1,2} <$ 1.2 TeV
+\end{itemize}
+
+where $E_{visible}$ is the total energy of the jets and $E_{top,i}$ is the energy of the $i^{th}$ top quark.
+99$\%$ of the signal events passed the cut whereas for the background 70$\%$.
+
+In what follows I enumerate the input variables in the TMVA that they were used for trainning and testing 
+the classifiers. It is important to notice that the sample with which the BDT's was trainned and tested were
+different.
+
+\begin{enumerate}
+ \item The invariant masses of the top quarks
+ \item The invariant masses of the W bosons
+ \item The missing transverse momentum  $p_{T}$
+ \item The $\Delta \phi$ angle between the $t\bar{}t$ quarks
+ \item The $\Delta R$  between the W candidates and the b jets
+ \item The $cos\theta_{top}$. We expect the top quarks created by purely SM processes to be more boosted 
+ than the ones that involved SUSY processes.
+ \item Thrust: 
+ \begin{equation}
+  T=max_{\hat{n}}\frac{\sum_{i}^{}|\vec{p}_{i}\cdot \hat{n}_{i}|}{\sum_{i}^{}|\vec{p}_{i}|}
+ \end{equation}
+	where $\hat{n}$ is the unitary vector that maximises the ratio of the sums. The sums run over all the
+	particles that emerge from the collision.
+
+  \item The three highest b tags
+  \item The three highest c tags
+  \item $\theta_{miss}$, which is defined to be the polar angle of the missing momentum
+  \item Oblatness
+  \item Sphericity (defined in~\cite{chen2012new})
+  \item Aplanarity (defined in~\cite{chen2012new})
+  \item The number of particles
+  \item $y_{3,4},y_{4,5},y_{5,6},y_{6,7},y_{7,8}$: The jet transition values defined from the following 
+  formula:
+  \begin{equation}
+   y_{i,j}=min(E_{i}^{2},E_{j}^{2})\frac{1-(cos\theta_{i}-cos\theta_{j})}{s}
+  \end{equation}
+  where i,j jets are chosen such that y gets the minimum value. 
+\end{enumerate}
+
+\newpage
+
+The TMVA trains the classifiers with respect to the input variables and then with the weight files that it has
+created, it applies them to a different sample (test phase). Essentially what TMVA achieves is reducing the 
+multi dimantional phase space of variables into one variable, known as BDT cut.
+
+According to the following graph, the value of the BDT cut that was chosen is $cut_{BDT}=-0.036$ due to the 
+fact that it has the maximum statistical significance $\frac{S}{\sqrt{S+B}}$=5.68, where S is the
+number of signal events and B is the number of background events.
+
+\begin{figure}[ht!]
+  \includegraphics[width=0.6\linewidth]{{images/cut_efficiency}.pdf}
+  \caption{The green line represents the statistical significance $\frac{S}{\sqrt{S+B}}$ where as it can be
+  seen it reaches the greatest value at -0.036. The cut is also known as descision boundary and defines the
+  critical region.}
+
+ \includegraphics[width=0.6\linewidth]{{images/BDT_output}.pdf}
+  \caption{The BDT output for the signal and the two backgrounds. The y axis has a log scale.}
+\end{figure}
+
+\newpage
+
+After the training phase, the TMVA yields which variables where the most important in the classification
+procedure where (ordered from the most significant):
+
+\begin{enumerate}
+ \item $\theta_{miss}$
+ \item missing $p_{T}$ 
+ \item $\Delta \phi$
+ \item $cos\theta_{top}$
+\end{enumerate}
+
+The following histograms show the aforementioned variables as they were given for training and testing.
+
+\begin{figure}
+\begin{minipage}[c]{0.5\linewidth}
+\includegraphics[width=\linewidth]{{images/thetamiss_report}.pdf}
+\caption{\scriptsize{Polar angle of the missing momentum of the jets}}
+\end{minipage}
+\hfill
+\begin{minipage}[c]{0.5\linewidth}
+\includegraphics[width=\linewidth]{{images/missingptpfo_report}.pdf}
+\caption{\scriptsize{Missing transverse momentum}}
+\end{minipage}
+\end{figure}
+
+\begin{figure}
+\begin{minipage}[c]{0.5\linewidth}
+\includegraphics[width=\linewidth]{{images/deltaphi_report}.pdf}
+\caption{\scriptsize{The angle between the reconstructed tops}}
+\end{minipage}
+\hfill
+\begin{minipage}[c]{0.5\linewidth}
+\includegraphics[width=\linewidth]{{images/costhetatopmax}.pdf}
+\caption{\scriptsize{cos$\theta_{top}$}}
+\end{minipage}
+\end{figure}
+
+\newpage
+
 \chapter{Results and Analysis}

### 2017-08-05 Tex_Dissertation/MSc_dissertation.tex
post tragedy

@@
   \includegraphics[width=0.7\linewidth]{{images/beamsstrahlung}.png}
-  \caption{The luminosity spectrum for CLIC operating at $\surd s$ = 3 TeV, where $\surd s'$ is the
-  effective centre-of-mass energy after beamstrahlung and initial state radiation }
+  \caption{\scriptsize{The luminosity spectrum for CLIC operating at $\surd s$ = 3 TeV, where $\surd s'$ is the
+  effective centre-of-mass energy after beamstrahlung and initial state radiation.}}
   \label{fig2.15}
@@
 
+Further more
+
 \chapter{Methods}
@@
 analysis platform in order (for this project) to make separation between the signal and the background. Two 
-of them were empoyed and used and compaired: the \textit{Boosted Descision Trees} (BDT) and the 
+of them were empoyed, used and compaired: the \textit{Boosted Descision Trees} (BDT) and the 
 \textit{Gradient Boosted Descision Trees} (GBDT).
@@
 Suppose we start with signal and background events described by a set of variables such as (in HEP) transverse 
-momenta, missing energy, etc. Then we sort all events by each variable and we choose the one that gives the
-best separation between signal and background. This is how the first node is made. Then, in the two branches 
+momenta, missing energy, etc. Then TMVA sorts all events by each variable and we choose the one that gives the
+best separation between signal and background. This is how the first node is made called root. Then, in the two branches 
 that are made we repeat this procedure applying the best cut on each node until the splitting stops based on 
@@
 
-In the physical case that I examine I have what will later be denoted as SUSY signal: corresponding to the 
+In the physical case that I examine what will later be denoted as SUSY signal: corresponding to the 
 top squarks, SUSY and SM background: corresponding to any physical process that immitates the one under 
@@
   \includegraphics[width=0.6\linewidth]{{images/cut_efficiency}.pdf}
-  \caption{The green line represents the statistical significance $\frac{S}{\sqrt{S+B}}$ where as it can be
+  \caption{\scriptsize{The green line represents the statistical significance $\frac{S}{\sqrt{S+B}}$ where as it can be
   seen it reaches the greatest value at -0.036. The cut is also known as descision boundary and defines the
-  critical region.}
+  critical region.}}
 
  \includegraphics[width=0.6\linewidth]{{images/BDT_output}.pdf}
-  \caption{The BDT output for the signal and the two backgrounds. The y axis has a log scale.}
+  \caption{\scriptsize{The BDT output for the signal and the two backgrounds. The y axis has a log scale.}}
 \end{figure}
@@
 
-The following histograms show the aforementioned variables as they were given for training and testing.
+The above histograms show the aforementioned variables as they were given for training and testing.
 
@@
 \newpage
+
+\subsubsection{Energy Spectrum of the Reconstructed Top quark}
+
+In the histogram below the energy spectrum of the top quark can be seen for the signal events.
+This variable was not given to the TMVA for training and testing. 
+It is clear that the maximum value of the energy is 1200 Tev something that explains why this was also set  
+as a preselection cut.
+
+\begin{figure}[ht!]
+  \includegraphics[width=0.7\linewidth]{{images/E_jjj}.pdf}
+  \caption{\scriptsize{The energy of the top quark. For higher energies there are less entries per bin, something that
+  is connected with the effect of Beamsstrahlung radiadion that is manifested mainly in higher energies.}}
+\end{figure}
+
+\begin{figure}[ht!]
+  \includegraphics[width=0.7\linewidth]{{images/ratio_plot_witherrors}.pdf}
+  \caption{\scriptsize{}}
+\end{figure}
+
+In the above histogram it can be seen the signal efficiency (with errors) as with respect to the energy of the three jets
+$E_{jjj}$. It is defined to be the ratio of the number of events that passed the $cut_{BDT}$ over the total
+number of the signal events.
+
+For completenes, the above diagrams depict the SM background efficiency and the SUSY background efficiency.
+
+\begin{figure}
+\begin{minipage}[c]{0.5\linewidth}
+\includegraphics[width=\linewidth]{{images/ratio_plot_SMbackground_witherrors}.pdf}
+\caption{\scriptsize{The Standard Model Background Efficiency}}
+\end{minipage}
+\hfill
+\begin{minipage}[c]{0.5\linewidth}
+\includegraphics[width=\linewidth]{{images/ratio_plot_susybg_witherrors}.pdf}
+\caption{\scriptsize{The SUSY Background Efficiency}}
+\end{minipage}
+\end{figure}
+
+\newpage
+
+\subsubsection{Effectiveness of BDT's}
+
+In the following graphs we can see the number of events of the signal and the two backgrounds with respect
+of the $E_{jjj}$.
+
+\begin{figure}[ht!]
+  \includegraphics[width=0.7\linewidth]{{images/ratio_plot_witherrors}.pdf}
+  \caption{\scriptsize{}}
+\end{figure}
 

### 2017-08-05 Tex_Dissertation/MSc_dissertation.tex
saturday

@@
 1.5 & 1.5 ab$^{-1}$ \\
-3   &  2 ab$^{-1}$ 
+3   &  3 ab$^{-1}$ 
  %inserts single line
@@
 \begin{figure}
-\begin{minipage}[c]{0.5\linewidth}
+\begin{minipage}[c]{0.6\linewidth}
 \includegraphics[width=\linewidth]{{images/ratio_plot_SMbackground_witherrors}.pdf}
@@
 \hfill
-\begin{minipage}[c]{0.5\linewidth}
+\begin{minipage}[c]{0.6\linewidth}
 \includegraphics[width=\linewidth]{{images/ratio_plot_susybg_witherrors}.pdf}
@@
 In the following graphs we can see the number of events of the signal and the two backgrounds with respect
-of the $E_{jjj}$.
+of the $E_{jjj}$ before and after the $cut_{BDT}$. As it can be seen, the Standard Model Background as well as
+the SUSY Background have reduced significantly.
 
 \begin{figure}[ht!]
-  \includegraphics[width=0.7\linewidth]{{images/ratio_plot_witherrors}.pdf}
-  \caption{\scriptsize{}}
-\end{figure}
+  \includegraphics[width=0.7\linewidth]{{images/prebdtcut}.pdf}
+  \caption{\scriptsize{Signal, SM background and SUSY background before the TMVA application. It is a 
+  stacked histogram with log y axis.}}
+\end{figure}
+
+\begin{figure}[ht!]
+  \includegraphics[width=0.7\linewidth]{{images/postbdtcut}.pdf}
+  \caption{\scriptsize{Signal, SM background and SUSY background after the TMVA application.}}
+\end{figure}
+
+\newpage
+
+The following table summarises the number of events that passed the preselection cuts, before and after the 
+TMVA cut.
+
+\begin{table}[h]
+
+\centering % used for centering table
+\begin{tabular}{||c | c | c||} % centered columns (4 columns)
+\hline %inserts double horizontal lines
+Before TMVA (Number of events)  & After TMVA (Number of events) & $\%$  \\ \hline % inserts single horizontal line
+3005   & 542    & 18 \\
+17628  & 567    &  3 \\
+113494 &  3036  &  2 \\  
+\hline
+ %inserts single line
+\end{tabular}
+\label{table:nonlin} % is used to refer this table in the text
+\end{table}
+
+\subsubsection{Mass Calculation Results}
 

### 2017-08-06 Tex_Dissertation/MSc_dissertation.tex
new

@@
  \mathcal{M}^{2}_{\tilde{f}} =
+
  \[  
@@
 \subsubsection{Mass Calculation Results}
+
+For the calculation of the top squark mass I made use of the minimisation of the $\chi^{2}$ method. In this 
+method we calculate the $\chi^{2}$ value for different masses of the top squark, and the minimum of the fitted
+polynomial yields the mass.
+
+Concretely, the formula for the calculation of the $\chi^{2}$ is:
+
+\begin{equation}
+ \chi^{2}=\sum_{i}^{}\frac{(n_{data,i}-n_{template,i})^{2}}{\sigma_{data,i}^{2}+\sigma_{template,i}^{2}}
+\end{equation}
+
+where $n_{data}$ are the number of events in the energy spectrum of the three jets after the TMVA (figure 4.12)
+and $n_{template}$ are the number of events for each different template, while the sum runs over all the bins
+of the histogram.. Those are summarised in the table below.
+
+\hfill
+
+\centering % used for centering table
+\begin{tabular}{||c | c||} % centered columns (4 columns)
+\hline \hline %inserts double horizontal lines
+$M_{template}$ 		   & $\sigma$ (fb)   \\ \hline % inserts single horizontal line
+$M_{nom}$ -200 GeV         &   2.8   \\
+$M_{nom}$ -100 GeV         &   2.2   \\
+$M_{nom}$ -50  GeV         &   1.9   \\  
+$M_{nom}$        	   &  1.65   \\
+$M_{nom}$ +50  GeV	   &   1.4   \\
+$M_{nom}$ +100 GeV	   &   1.2   \\
+$M_{nom}$ +200 GeV	   &   0.8   \\
+
+\hline
+ %inserts single line
+\end{tabular}
+\label{table:nonlin} % is used to refer this table in the text
+\end{table}
 

### 2017-08-06 Tex_Dissertation/MSc_dissertation.tex
results

@@
 and $n_{template}$ are the number of events for each different template, while the sum runs over all the bins
-of the histogram.. Those are summarised in the table below.
+of the histogram. The templates are summarised in the table below.
 
@@
 
+\begin{table}[h]
 \centering % used for centering table
@@
 \end{table}
+
+\newpage
+
+\begin{figure}[ht!]
+\centering
+  \includegraphics[width=0.7\linewidth]{{images/chisqvsmass_intlumi3000}.pdf}
+  \caption{\scriptsize{The $\chi^{2}$ versus the different top squark mass templates.}}
+\end{figure}
+
+In order to calculate the statistical uncertainty off the mass we employed a \textit{toy Monte Carlo Method}.
+
+In this method, I smeared each bin of the energy spectrum of the three jets (Figure 4.12), with a Gaussian
+of deviation $\sqrt{n_{data,i}}$ and mean zero. Then the mass calculation was repeated. This procedure was 
+done 5000 times. The deviation of the Gaussian was chosen to have that value since $\sqrt{n_{data,i}}$
+is the error of each bin content $i$. The result was an uncertainty of the mass 14 GeV.
+
+\begin{figure}[ht!]
+\centering
+  \includegraphics[width=0.7\linewidth]{{images/toyMC_intlumi3000}.pdf}
+  \caption{\scriptsize{Toy Monte carlo method that yielded an uncertainty of 14 GeV.}}
+\end{figure}
+
+\newpage
+
+\subsection{Results - Summary of the BDT method}
 

### 2017-08-06 Tex_Dissertation/MSc_dissertation.tex
finishedbdt

@@
   \includegraphics[width=0.7\linewidth]{{images/postbdtcut}.pdf}
-  \caption{\scriptsize{Signal, SM background and SUSY background after the TMVA application.}}
+  \caption{\scriptsize{Signal, SM background and SUSY background after the TMVA application, again stacked.}}
 \end{figure}
@@
 and $n_{template}$ are the number of events for each different template, while the sum runs over all the bins
-of the histogram. The templates are summarised in the table below.
+of the histogram. A $\chi^{2}$ was calculated for each different template, summarised in the table below.
 
@@
 
+The mass was found  to be $m_{\tilde{t}}$ = 860 GeV.
+
 \newpage
@@
   \includegraphics[width=0.7\linewidth]{{images/chisqvsmass_intlumi3000}.pdf}
-  \caption{\scriptsize{The $\chi^{2}$ versus the different top squark mass templates.}}
+  \caption{\scriptsize{The $\chi^{2}$ versus the different top squark mass templates. The minimum is at 
+  860 GeV/c$^{2}$.}}
 \end{figure}
@@
 \subsection{Results - Summary of the BDT method}
+
+Using the Boosted Descision Trees and with the method of minimisation of the $\chi^{2}$ for different 
+templates, I found the mass of the supersymmetric top quark to be
+
+\begin{equation}
+ m_{\tilde{t}}=860\pm 14 \textrm{GeV}/c^{2}
+\end{equation}
+
+Although the nominal mass is $M_{nom}$= 846 GeV/$c^{2}$, my calculation is one sigma  inside this range,
+taking into account the aforementioned uncertainty at CLIC for integrated luminosity 
+$\mathcal{L}_{int}$=3000 fb$^{-1}$.
+
+\newpage
+
+\subsection{Classification Method: \textit{Gradient Boosted Descision Trees}}
 

### 2017-08-07 Tex_Dissertation/MSc_dissertation.tex
end_of_day
gbdttheory

@@
   \centering
-  \includegraphics[width=0.7\linewidth, scale=5]{{images/fig_08}.png}
+  \includegraphics[width=0.6\linewidth, scale=5]{{images/fig_08}.png}
   \label{}
 \end{figure}
-
-Further more
 
@@
 
+In this chapter I will describe the mass calculation for the top squark using the Gradient Boosted 
+Decision Trees (GBDT) as a method of classification for discrimination between signal and background. Furthermore,
+comparison will be made between BDT's and GBDT's.
+
+\subsubsection{Background on GBDT's}
+
+Gradient Boosting is a different method for classification. The goal, as in the BDT's, is to create a 
+prediction model. The main difference from the classification method described in chapter 4.3.4 is that 
+the prediction model is built in an iterative way allowing its own optimisation by the calculation of errors.
+
+Again like all the boosting methods, it combines a set of weak learners (for BDT it was the number of trees).
+In the first phase -training phase- a rough approximation for the prediction model is made. Subsequently, the error of the 
+the error of the model and the actual values expected, is calculated (residual) and it is added in the
+previous model making it a slightly  better compaired to the previous one. 
+This procedure is repeated various times.
+
+The name gradient comes from the observation that the residuals that each time are added are just the 
+negative gradient of a squared error loss function~\cite{hoecker2007tmva}.
+
 \chapter{Results and Analysis}
@@
 Here are some results.
-
-\subsection{More results}
-When showing results you are likely to use tables and graphs. You can
-create tables easily in \LaTeX.
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{||l|c|l||}
-\hline
-\textbf{File names} & \textbf{Satellite} & \textbf{Resolution}\\
-\hline
-  worldr            &  Meteosat          &   5km\\
-  worldg            &  Meteosat          &   5km\\
-  worldb            &  Meteosat          &   5km\\
-\hline
-\end{tabular}
-\end{center}
-\caption{This is a simple table. More complicated tables can have
-headings which pass over more than one column}
-\label{simple_table}
-\end{table}
-
-If you want to produce fancier tables than shown in Table \ref{simple_table}
-refer to the \LaTeX\ manual or ask Google.
-
-One of the simplest ways to produce simple graphs is to use gnuplot
-which produces \LaTeX\  output. Graph~(\ref{fig:gnu}) was produced using
-gnuplot with output designated as \LaTeX\  so that a \LaTeX\  output file is
-produced which you can include directly or keep separate and refer to
-using the \emph{include} command.
-
-Another approach is to draw simple figures using \emph{xfig} which allows
-you to export diagrams in \LaTeX\  picture format so that the diagram can
-be included directly.
-
-Perhaps the most robust way to include graphs is to convert them to
-PostScript or PDF and include them in the same was as was done in
-Figure~\ref{fig:eucrest} for the University Crest. You can usually do
-this with most packages, including Microsoft ones; one trick for
-producing PostScript is to print to a dummy PostScript printer.
-
-% in practice you would probably keep this in a separate file and use
-% the \include{filename} command to insert it here.
-
-\begin{figure}
-% GNUPLOT: LaTeX picture
-\setlength{\unitlength}{0.240900pt}
-\ifx\plotpoint\undefined\newsavebox{\plotpoint}\fi
-\sbox{\plotpoint}{\rule[-0.200pt]{0.400pt}{0.400pt}}%
-\begin{picture}(1500,1200)(0,0)
-\font\gnuplot=cmr10 at 10pt
-\gnuplot
-\sbox{\plotpoint}{\rule[-0.200pt]{0.400pt}{0.400pt}}%
-\put(220.0,113.0){\rule[-0.200pt]{292.934pt}{0.400pt}}
-\put(220.0,113.0){\rule[-0.200pt]{0.400pt}{245.477pt}}
-\put(220.0,113.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(198,113){\makebox(0,0)[r]{$0$}}
-\put(1416.0,113.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(220.0,317.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(198,317){\makebox(0,0)[r]{$0.2$}}
-\put(1416.0,317.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(220.0,521.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(198,521){\makebox(0,0)[r]{$0.4$}}
-\put(1416.0,521.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(220.0,724.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(198,724){\makebox(0,0)[r]{$0.6$}}
-\put(1416.0,724.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(220.0,928.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(198,928){\makebox(0,0)[r]{$0.8$}}
-\put(1416.0,928.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(220.0,1132.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(198,1132){\makebox(0,0)[r]{$1$}}
-\put(1416.0,1132.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(220.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(220,68){\makebox(0,0){$0$}}
-\put(220.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(414.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(414,68){\makebox(0,0){$1$}}
-\put(414.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(607.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(607,68){\makebox(0,0){$2$}}
-\put(607.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(801.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(801,68){\makebox(0,0){$3$}}
-\put(801.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(995.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(995,68){\makebox(0,0){$4$}}
-\put(995.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(1188.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(1188,68){\makebox(0,0){$5$}}
-\put(1188.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(1382.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(1382,68){\makebox(0,0){$6$}}
-\put(1382.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(220.0,113.0){\rule[-0.200pt]{292.934pt}{0.400pt}}
-\put(1436.0,113.0){\rule[-0.200pt]{0.400pt}{245.477pt}}
-\put(220.0,1132.0){\rule[-0.200pt]{292.934pt}{0.400pt}}
-\put(45,622){\makebox(0,0){\shortstack{This is\\the\\$y$ axis}}}
-\put(828,23){\makebox(0,0){This is the $x$ axis}}
-\put(828,1177){\makebox(0,0){This is a plot of $y=sin(x)$}}
-\put(220.0,113.0){\rule[-0.200pt]{0.400pt}{245.477pt}}
-\sbox{\plotpoint}{\rule[-0.500pt]{1.000pt}{1.000pt}}%
-\put(1306,1067){\makebox(0,0)[r]{sin(x)}}
-\multiput(1328,1067)(20.756,0.000){4}{\usebox{\plotpoint}}
-\put(1394,1067){\usebox{\plotpoint}}
-\put(220,113){\usebox{\plotpoint}}
-\multiput(220,113)(3.768,20.411){4}{\usebox{\plotpoint}}
-\multiput(232,178)(4.132,20.340){3}{\usebox{\plotpoint}}
-\multiput(245,242)(3.825,20.400){3}{\usebox{\plotpoint}}
-\multiput(257,306)(3.884,20.389){3}{\usebox{\plotpoint}}
-\multiput(269,369)(3.944,20.377){3}{\usebox{\plotpoint}}
-\multiput(281,431)(4.326,20.300){3}{\usebox{\plotpoint}}
-\multiput(294,492)(4.137,20.339){3}{\usebox{\plotpoint}}
-\multiput(306,551)(4.276,20.310){3}{\usebox{\plotpoint}}
-\multiput(318,608)(4.693,20.218){3}{\usebox{\plotpoint}}
-\multiput(331,664)(4.583,20.243){2}{\usebox{\plotpoint}}
-\multiput(343,717)(4.754,20.204){3}{\usebox{\plotpoint}}
-\multiput(355,768)(5.034,20.136){2}{\usebox{\plotpoint}}
-\multiput(367,816)(5.760,19.940){2}{\usebox{\plotpoint}}
-\multiput(380,861)(5.579,19.992){3}{\usebox{\plotpoint}}
-\put(398.00,923.50){\usebox{\plotpoint}}
-\multiput(404,943)(7.049,19.522){2}{\usebox{\plotpoint}}
-\multiput(417,979)(7.288,19.434){2}{\usebox{\plotpoint}}
-\put(433.18,1021.10){\usebox{\plotpoint}}
-\multiput(441,1040)(8.982,18.712){2}{\usebox{\plotpoint}}
-\put(460.41,1076.97){\usebox{\plotpoint}}
-\put(471.84,1094.28){\usebox{\plotpoint}}
-\put(484.84,1110.41){\usebox{\plotpoint}}
-\put(500.42,1124.01){\usebox{\plotpoint}}
-\multiput(503,1126)(19.159,7.983){0}{\usebox{\plotpoint}}
-\put(519.48,1131.37){\usebox{\plotpoint}}
-\multiput(527,1132)(20.136,-5.034){0}{\usebox{\plotpoint}}
-\put(539.74,1128.60){\usebox{\plotpoint}}
-\put(557.04,1117.38){\usebox{\plotpoint}}
-\put(570.79,1101.95){\usebox{\plotpoint}}
-\put(582.44,1084.80){\usebox{\plotpoint}}
-\put(593.09,1066.99){\usebox{\plotpoint}}
-\multiput(601,1053)(8.430,-18.967){2}{\usebox{\plotpoint}}
-\put(619.18,1010.54){\usebox{\plotpoint}}
-\multiput(625,996)(7.413,-19.387){2}{\usebox{\plotpoint}}
-\multiput(638,962)(6.403,-19.743){2}{\usebox{\plotpoint}}
-\multiput(650,925)(5.830,-19.920){2}{\usebox{\plotpoint}}
-\multiput(662,884)(5.461,-20.024){2}{\usebox{\plotpoint}}
-\multiput(674,840)(5.533,-20.004){2}{\usebox{\plotpoint}}
-\multiput(687,793)(4.937,-20.160){3}{\usebox{\plotpoint}}
-\multiput(699,744)(4.667,-20.224){2}{\usebox{\plotpoint}}
-\multiput(711,692)(4.858,-20.179){3}{\usebox{\plotpoint}}
-\multiput(724,638)(4.276,-20.310){3}{\usebox{\plotpoint}}
-\multiput(736,581)(4.205,-20.325){3}{\usebox{\plotpoint}}
-\multiput(748,523)(4.070,-20.352){3}{\usebox{\plotpoint}}
-\multiput(760,463)(4.326,-20.300){3}{\usebox{\plotpoint}}
-\multiput(773,402)(3.884,-20.389){3}{\usebox{\plotpoint}}
-\multiput(785,339)(3.884,-20.389){3}{\usebox{\plotpoint}}
-\multiput(797,276)(4.070,-20.352){3}{\usebox{\plotpoint}}
-\multiput(810,211)(3.825,-20.400){3}{\usebox{\plotpoint}}
-\multiput(822,147)(3.607,-20.440){2}{\usebox{\plotpoint}}
-\put(828,113){\usebox{\plotpoint}}
-\end{picture}
-\caption{Simple Gnuplot example}
-\label{fig:gnu}
-\end{figure}
 

### 2017-08-07 Tex_Dissertation/MSc_dissertation.tex
endofday

@@
 prediction model. The main difference from the classification method described in chapter 4.3.4 is that 
-the prediction model is built in an iterative way allowing its own optimisation by the calculation of errors.
+the prediction model is built in an iterative way allowing its own optimisation by the calculation of errors
+using a different loss function.
 
@@
 The name gradient comes from the observation that the residuals that each time are added are just the 
-negative gradient of a squared error loss function~\cite{hoecker2007tmva}.
+negative gradient of a squared error loss function~\cite{hoecker2007tmva}. The mathematical formulation of 
+both BDT's and GBDT's lies beyond the scope of this project but it can be seen in~\cite{schapire1999brief},
+~\cite{hoecker2007tmva}.
 

### 2017-08-08 Tex_Dissertation/MSc_dissertation.tex
waitforresults

--- 2017-08-07 Tex_Dissertation/MSc_dissertation.tex
@@
 \begin{figure}[ht!]
-  \includegraphics[width=0.6\linewidth]{{images/cut_efficiency}.pdf}
+  \includegraphics[width=0.6\linewidth]{{images/cutefficiences_1000trees2}.pdf}
   \caption{\scriptsize{The green line represents the statistical significance $\frac{S}{\sqrt{S+B}}$ where as it can be
-  seen it reaches the greatest value at -0.036. The cut is also known as descision boundary and defines the
+  seen it reaches the greatest value at -0.0238. The cut is also known as descision boundary and defines the
   critical region.}}
 
- \includegraphics[width=0.6\linewidth]{{images/BDT_output}.pdf}
+ \includegraphics[width=0.6\linewidth]{{images/BDT_output_intlum3000}.pdf}
   \caption{\scriptsize{The BDT output for the signal and the two backgrounds. The y axis has a log scale.}}
@@
 \begin{figure}[ht!]
-  \includegraphics[width=0.7\linewidth]{{images/postbdtcut}.pdf}
+  \includegraphics[width=0.7\linewidth]{{images/postbdtcut_intlumi3000}.pdf}
   \caption{\scriptsize{Signal, SM background and SUSY background after the TMVA application, again stacked.}}
@@
 Before TMVA (Number of events)  & After TMVA (Number of events) & $\%$  \\ \hline % inserts single horizontal line
-3005   & 542    & 18 \\
-17628  & 567    &  3 \\
-113494 &  3036  &  2 \\  
+3005   & 493    & 16 \\
+17628  & 558    &  3.1 \\
+113494 &  528  &  0.4 \\  
 \hline
@@
 
-The mass was found  to be $m_{\tilde{t}}$ = 860 GeV.
+The mass was found  to be $m_{\tilde{t}}$ = 839 GeV.
 
@@
   \includegraphics[width=0.7\linewidth]{{images/toyMC_intlumi3000}.pdf}
-  \caption{\scriptsize{Toy Monte carlo method that yielded an uncertainty of 14 GeV.}}
+  \caption{\scriptsize{Toy Monte carlo method that yielded an uncertainty of 11 GeV.}}
 \end{figure}
@@
 \begin{equation}
- m_{\tilde{t}}=860\pm 14 \textrm{GeV}/c^{2}
-\end{equation}
-
-Although the nominal mass is $M_{nom}$= 846 GeV/$c^{2}$, my calculation is one sigma  inside this range,
+ m_{\tilde{t}}=839\pm 11 \textrm{GeV}/c^{2}
+\end{equation}
+
+Although the nominal mass is $M_{nom}$= 845 GeV/$c^{2}$, my calculation is one sigma  inside this range,
 taking into account the aforementioned uncertainty at CLIC for integrated luminosity 
@@
 prediction model. The main difference from the classification method described in chapter 4.3.4 is that 
-the prediction model is built in an iterative way allowing its own optimisation by the calculation of errors.
+the prediction model is built in an iterative way allowing its own optimisation by the calculation of errors
+using a different loss function (than the one used for the BDT's).
 
 Again like all the boosting methods, it combines a set of weak learners (for BDT it was the number of trees).
-In the first phase -training phase- a rough approximation for the prediction model is made. Subsequently, the error of the 
-the error of the model and the actual values expected, is calculated (residual) and it is added in the
-previous model making it a slightly  better compaired to the previous one. 
-This procedure is repeated various times.
+In the first phase -training phase- a rough approximation for the prediction model is made. Subsequently, the 
+the error of the model and the actual values expected is calculated (residual) and it is added in the
+previous model making it a slightly  better. This procedure is repeated various times until a good description
+is reached.
 
 The name gradient comes from the observation that the residuals that each time are added are just the 
-negative gradient of a squared error loss function~\cite{hoecker2007tmva}.
+negative gradient of a squared error loss function~\cite{hoecker2007tmva}. The mathematical formulation of 
+both BDT's and GBDT's lies beyond the scope of this project but can be seen in~\cite{schapire1999brief},
+~\cite{hoecker2007tmva}.
+
+\subsubsection{Training and testing phase}
+
+In this part of the procedure I "fed" the TMVA with the exact same variables as I did for the BDT's and 
+imposed the exact same preselection cuts. The purpose of this is to make a comparison of the two methods in 
+the end.
+
+The preselection cuts were:
+
+\begin{itemize}
+ \item $E_{visible} <$ 2 TeV
+ \item $E_{top1,2} <$ 1.2 TeV
+\end{itemize}
+
+The list of the input variables can be seen in chapter 4.3.4 (p.16).
+
+Based again, to the graph that has the efficiency vs the $cut_{GBDT}$, the chosen value for the cut was the one
+that maximised the statistical significance $\frac{S}{\sqrt{S+B}}$, where $S$ is the signal and $B$ is the 
+background: $cut_{GBDT}=-0.0606$. It needs to be noted that the statistical significance achieved through
+this method is almost one point higher than that of the BDT method of classification.
+
+\begin{figure}[ht!]
+\centering
+  \includegraphics[width=0.7\linewidth]{{images/cutefficiency_bdtg_new}.pdf}
+  \caption{\scriptsize{The green line represents the statistical significance $\frac{S}{\sqrt{S+B}}$ where as it can be
+  seen it reaches the greatest value at -0.0606. The cut is also known as descision boundary and defines the
+  critical region.}}
+\end{figure}
 

### 2017-08-08 Tex_Dissertation/MSc_dissertation.tex
afterresults

@@
 
-\begin{table}[h]
-
+\begin{table}
 \centering % used for centering table
-\begin{tabular}{||c | c | c||} % centered columns (4 columns)
+\begin{tabular}{||c | c | c | c||} % centered columns (4 columns)
 \hline %inserts double horizontal lines
-Before TMVA (Number of events)  & After TMVA (Number of events) & $\%$  \\ \hline % inserts single horizontal line
-3005   & 493    & 16 \\
-17628  & 558    &  3.1 \\
-113494 &  528  &  0.4 \\  
+       BDT      &Before TMVA ($N_{events}$)  & After TMVA ($N_{events}$) & $\%$  \\ \hline % inserts single horizontal line
+Signal           & 3005     &  493       & 16 \\
+SUSY background  & 17628    &  558       & 3.1 \\
+SM background    & 113494   &  528       &  0.4 \\  
 \hline
@@
 \end{figure}
+
+The variables that TMVA found most important are exactly the same with those of the BDT method, namely:
+
+\begin{enumerate}
+ \item $\theta_{miss}$ : the polar angle of the missing momentum of the jets.
+ \item $p_{T}$ : the missing transverse momentum.
+ \item $\Delta \phi$ : the angle between the reconstructed tops.
+ \item $cos\theta_{top}$.
+\end{enumerate}
+
+In the following stacked histogram, it can be seen the post GBDT reduction of background and in the table 
+above, the number of events that passed (for both signal and background) are denoted.
+
+\newpage
+
+\begin{figure}[ht!]
+\centering
+  \includegraphics[width=0.8\linewidth]{{images/postbdtcut_gbdt}.pdf}
+  \caption{\scriptsize{}}
+\end{figure}
+
+\begin{table}
+\centering % used for centering table
+\begin{tabular}{||c | c | c | c||} % centered columns (4 columns)
+\hline %inserts double horizontal lines
+       GBDT      &Before TMVA ($N_{events}$)  & After TMVA ($N_{events}$) & $\%$  \\ \hline % inserts single horizontal line
+Signal           & 3005     & 455       & 15 \\
+SUSY background  & 17628    &  330      & 1.8 \\
+SM background    & 113494   &  198      &  0.1 \\  
+\hline
+ %inserts single line
+\end{tabular}
+\label{table:nonlin} % is used to refer this table in the text
+\end{table}
 

### 2017-08-09 Tex_Dissertation/MSc_dissertation.tex
lastoftheday
almost

@@
 the prediction model is built in an iterative way allowing its own optimisation by the calculation of errors
-using a different loss function (than the one used for the BDT's).
+using a different loss function than the one used for the BDT's.
 
@@
 In the first phase -training phase- a rough approximation for the prediction model is made. Subsequently, the 
-the error of the model and the actual values expected is calculated (residual) and it is added in the
+the error of the model and the actual expected values is calculated (residual) and it is added in the
 previous model making it a slightly  better. This procedure is repeated various times until a good description
@@
 imposed the exact same preselection cuts. The purpose of this is to make a comparison of the two methods in 
-the end.
+the end. For this method 1000 trees were employed.
 
@@
 
-In the following stacked histogram, it can be seen the post GBDT reduction of background and in the table 
+In the following stacked histogram can be seen the post GBDT reduction of background and in the table 
 above, the number of events that passed (for both signal and background) are denoted.
@@
 \centering
-  \includegraphics[width=0.8\linewidth]{{images/postbdtcut_gbdt}.pdf}
-  \caption{\scriptsize{}}
+  \includegraphics[width=0.7\linewidth]{{images/postbdtcut_bdtg_3000}.pdf}
+  \caption{\scriptsize{Energy of the three jets after the $cut_{GBDT}$.}}
 \end{figure}
@@
 
-\chapter{Results and Analysis}
-
-This section should detail the obtained results in a clear,
-easy-to-follow manner. It is important to make clear what are original
-results and what are repeats of previous calculations or computations.
-Remember that long tables of numbers are just as boring to read as
-they are to type-in!
-
-Use graphs to present your results wherever practicable.
-
-Results or computations should be presented with uncertainties
-(errors), both statistical and systematic where applicable.
-
-Be selective in what you include: half a dozen \emph{e.g.}~tables that
-contain wrong data you collected while you forgot to switch on the
-computer are not relevant and may mask the correct results.
+\begin{figure}[!hb]
+\centering
+  \includegraphics[width=0.7\linewidth]{{images/GBDT_output}.pdf}
+  \caption{\scriptsize{The GBDT output for the signal (blue), SUSY background (red) and SM background 
+  (green).}}
+\end{figure}
+
+\newpage
+
+The above histograms show the effciency for both backgrounds whereas the one below, for the signal.
+\begin{figure}
+\begin{minipage}[c]{0.6\linewidth}
+\includegraphics[width=\linewidth]{{images/ratio_plot_SMbackground_witherrors_gbdt}.pdf}
+\caption{\scriptsize{The Standard Model Background Efficiency for the GBDT method.}}
+\end{minipage}
+\hfill
+\begin{minipage}[c]{0.6\linewidth}
+\includegraphics[width=\linewidth]{{images/ratio_plot_susybg_witherrors_gbdt}.pdf}
+\caption{\scriptsize{The SUSY Background Efficiency for the GBDT method.}}
+\end{minipage}
+\end{figure}
+
+\begin{figure}[!hb]
+\centering
+  \includegraphics[width=0.7\linewidth]{{images/ratio_plot_witherrors_gbdt}.pdf}
+  \caption{\scriptsize{The signal efficiency for the GBDT method.}}
+\end{figure}
+
+Using again the method of minimisation of the $\chi^{2}$ for different templates (table in p.22) of the top 
+squark mass (formula 4.9), I calculated the mass to be:
+\begin{equation}
+ m_{\tilde{t}}=811\quad \textrm{GeV}
+\end{equation}
+
+again using a toy Monte Carlo method I smeared each bin of the energy spectrum of the three jets with a 
+Gaussian of deviation $\sqrt{n_{data}}$ and mean zero, and I repeated the mass calculation. This procedure
+was done 5000 times. The resulting uncertainty was 19 GeV.
+
+Both calculations can be seen in the following graphs where in the first the minimisation of the $\chi^{2}$
+can be seen and in the second the calculation of the uncertainty.
+
+\begin{figure}[!hb]
+\centering
+  \includegraphics[width=0.7\linewidth]{{images/chisqvsmass_gbdt}.pdf}
+  \caption{\scriptsize{The $\chi^{2}$ versus the different mass templates. The minimum is at 811 GeV/$c^{2}$.}}
+\end{figure}
+
+\begin{figure}[!hb]
+\centering
+  \includegraphics[width=0.7\linewidth]{{images/toyMC_gbdt}.pdf}
+  \caption{\scriptsize{The resulting uncertaity from the toy Monte Carlo method is 15 GeV.}}
+\end{figure}
+
+\newpage
+
+\subsection{Results - Summary of the GBDT method}
+
+Using the Gradient Boosted Descision Trees and with the method of minimisation of
+the $\chi^{2}$ for different mass templates, I found the mass of the supersymmetric top
+quark to be:
+
+\begin{equation}
+ m_{\tilde{t}}=811\pm 15 \quad \textrm{GeV}
+\end{equation}
+
+The nominal mass is $M_{nom}$ = 845 GeV/$c^{2}$, my calculation is two sigma inside this range taking into 
+account the uncertainty calculated through the toy MC method at CLIC for an integrated luminosity
+$\mathcal{L}_{int}$=3000 fb$^{-1}$.
+
+\section{Comparison of BDT - GBDT methods/Results}
+
+In this section I am going to compaire the performance as well as the results of the two methods followed in
+this project.
+
+For the BDT method I set the number of weak learners (trees) to be 1000 and the maximum depth of the tree to 
+be 3. Same considarations took place also for the the GBDT method.
+
+The following table summarises the basic characteristics of the two methods:
+
+\begin{table}[!hb]
+\centering % used for centering table
+\begin{tabular}{||c | c | c | c||} % centered columns (4 columns)
+\hline %inserts double horizontal lines
+Method      &Stat. Efficiency &  $m_{\tilde{t}}$               &  $N_{signal}$ \\ 
+\hline 
+BDT         &       6.79      &  839 $\pm$ 11 GeV/$c^{2}$      &  493		\\
+GBD         &       7.68      &  811 $\pm$ 15 GeV/$c^{2}$      &  455		\\
+\hline
+ %inserts single line
+\end{tabular}
+\label{table:nonlin} % is used to refer this table in the text
+\end{table}
+
+As it can be seen the GBDT method achieves higher statistical significance in comparison with the BDT method
+but higher uncertainty with a difference of 4 GeV. This can be attributed to the fact that the proposed cuts 
+from the TMVA are mainly addressed for particle discoveries rather than for measuring an observable. That 
+means that for the optimal precision of the TMVA one has to "play" with the value of the cut -primarily
+around the proposed value - in order to extract the lowest uncertainty possible for the mass calculation.
+
+Although, apart from the "cut tunning" issue, the fact that the BDT's perform better than any other (so far)
+classification method is no new to the experimental world. From 2005 similar studies were made for the 
+MiniBoone experiment and it was found that
 

### 2017-08-09 Tex_Dissertation/MSc_dissertation.tex
afteer

@@
 around the proposed value - in order to extract the lowest uncertainty possible for the mass calculation.
-
-Although, apart from the "cut tunning" issue, the fact that the BDT's perform better than any other (so far)
-classification method is no new to the experimental world. From 2005 similar studies were made for the 
-MiniBoone experiment and it was found that
+Furthermore as it can be seen in the above graph, the number of events after the TMVA cut, in the case of 
+GBDT are almost 40 less. Even thought that they sound few, as a fraction they constitute 8$\%$ of the
+$N_{signal}$,
+number not at all negligible especially when we deal with a few hundreads of events.
+Additionally another interesting thing is the importance of these 40 more events in the case of BDT.
+This is cleat because in the BDT the number of events of SM background ($N_{events}$=528) 
+in total are far more 
+than those in the GBDT method ($N_{events}$=198), and at first sight it would be expected that the GBDT has 
+better potencial than the BDT. The mass and uncertainty measurements proved to be the other way round.
+
+Similar contradiccion produces the careful examination of the signal efficiency plots(4.8 for BDT and 4.20
+for GBDT). Both of them (taking into account the errors) tend to have an almost constant trend but the 
+efficiency of GBDT is higher.
+
+Although, apart from the "cut tunning" issue, the fact that the BDT's performance is superior is is no 
+new to the experimental world. From 2005, similar studies were made for the MiniBoone experiment and 
+it was found that BDT's (on Adaboost mode) outperform other methods~\cite{yang2005studies}.
 

### 2017-08-09 Tex_Dissertation/MSc_dissertation.tex
almost

@@
 \begin{abstract}
-In this project I calculate the mass of the Supersymmetric top quark in CLIC experiment at $\sqrt{s}$ = 3 TeV in $e^{-}$ $e^{+}$ collisions.
-I assume the following decay for the top squark $\tilde{q} \rightarrow q$ $\chi_{0}$,
-and I focus on the fully hadronic channel of decay i.e $\tilde{q} \rightarrow q$ $\chi_{0} \rightarrow$ $W b \tilde{\chi}_{1}^{0}$ .
-The mass was found  to be  $m_{\tilde{t}}$ = 861 $\pm$ 19 GeV using the Boosted Descision 
-Trees Multivariate Analysis and $m_{\tilde{t}}$ = 812 $\pm$ 20 GeV using the Gradient Boosted Descision  Trees Multivariate Analysis. 
+In this project I calculate the mass of the Supersymmetric top quark in CLIC experiment at $\sqrt{s}$ = 3 TeV
+and for an integrated luminosity $\mathcal{L}_{int}$=3000 fb$^{-1}$
+in $e^{-}$ $e^{+}$ collisions. I assume the following decay for the top squark $\tilde{q} \rightarrow q$ 
+$\chi_{0}$, 
+and the final products to be
+$\tilde{q} \rightarrow q$ $\chi_{0} \rightarrow$ $W b \tilde{\chi}_{1}^{0}$ .
+The mass was found  to be  $m_{\tilde{t}}$ = 839 $\pm$ 11 GeV/$c^{2}$ using the Boosted Descision 
+Trees Multivariate Analysis and $m_{\tilde{t}}$ = 861 $\pm$ 15 GeV/$c^{2}$ using the Gradient Boosted Descision  Trees Multivariate Analysis. 
 \end{abstract}
@@
 \textbf{Declaration}
+
+I declare that this project is a product of my own personal work.
 
@@
 
-Put your acknowledgements here. Thanking your supervisor for his/her
-help is standard practice, but you don't have to do this\ldots
-
-This template is is modification of the one for the MSc in High
-Performance Computing, which is apparently descended from a template
-developed by Prof Charles Duncan for MSc students in Meteorology. His
-acknowledgement follows:
-
-\emph{This template has been produced with help from many former
-  students who have shown different ways of doing things. Please make
-  suggestions for further improvements.}
-
-Some parts of this template were lifted unashamedly from the Edinburgh
-MPhys project report guide, with little or no modification. I have no
-idea who wrote the first version of that\ldots
-
-You don't have to use \LaTeX\ for your dissertation. You can use
-Microsoft Word or Apple Pages if you wish, but it's \emph{much} easier
-to typeset equations in \LaTeX, and references look after
-themselves. Whatever you use, your dissertation should have the same
-general structure, and it should look similar to this one --
-especially the front page.
+I would like to thank my supervisor Prof. Victoria J. Martin not only for her help, her patience and
+her deep and important insights on the subject, but also introducing me to a field that so far I was nothing 
+more than a stranger.
+
+Additionally I would like to express my gratitude towards the CLICdp team that helped me. Especially
+to Dr. Philipp Roloff, Dr. Marco Petric, Dr. Ignacio Garcia and Dr. Andre Sailer (all based at CERN).
 
@@
 
+-interesting---> N of trees
+
 Although, apart from the "cut tunning" issue, the fact that the BDT's performance is superior is is no 
@@
 
-\section{Some results}
-Here are some results.
-
-\section{Discussion of your results}
-
-This section should give a picture of what you have taken out of your
-project and how you can put it into context.
-
-This section should summarise the results obtained, detail conclusions
-reached, suggest future work, and changes that you would make if you
-repeated the project.
-
 \chapter{Conclusions}
 
-This is the place to put your conclusions about your work. You can
-split it into different sections if appropriate. You may want to include
-a section of future work which could be carried out to continue your
-research.
-
-The conclusion section should be at least one page long, preferably 2
-pages, but not much longer.
-
-\appendix
-% the appendix command just changes heading styles for appendices.
-
-\chapter{Stuff that's too detailed}
-
-Appendices should contain all the material which is considered too
-detailed to be included in the main body of the text, but which is
-important enough to be included in the thesis.
-
-Perhaps this is a good place to mention \BibTeX.
-
-You can do references in the simple way explained in the introduction,
-or you can use \BibTeX.
-
-\section{\BibTeX}
-\label{sec:bibtex}
-
-It is convenient to use \BibTeX\ to compile your bibliography.  First
-you need to create a .bib file e.g.  you may call it ref.bib Then you
-can put all your references into the file with entries such as
-\begin{verbatim}
-@Book{ob:bornwolf,
-     author = "Born, M and Wolf, E",
-     title  = "Principles of Optics",
-     publisher = "Cambridge University Press",
-     year = 1999,
-     edition = {7th},
-}
-
-@Article{jr:ashkin,
-Author = {A. Ashkin and J.M. Dziedzic and J.E. Bjorkholm and S. Chu},
-Title = "Observation of a single beam gradient force optical tap for 
-dielectric particles",
-Journal = "Optics Letters",
-Volume = 11,
-Pages = "288-290",
-Year = 1986}
-
-@INPROCEEDINGS{seger,
- author = {J. Seger and H.J. Brockman},
- title = {What is bet-hedging?},
- editors={P.H. Harvey and L. Partridge},
- booktitle = {Oxford Surveys in Evolutionary Biology},
- year={1987},
- page={18},
- publisher={Oxford University Press},
- place={Oxford}}
-\end{verbatim}
-for a book, an article in a journal or an article in a proceedings volume
-respectively.
-
-Inside your \LaTeX\ file
-you should include 
-\begin{verbatim}
-\bibliographystyle{unsrt}                      
-and
-\bibliography{ref}
-\end{verbatim}
-The first command determines the reference style, here plain and 
-unsorted. With this referencing style 
-a numerical referencing system (which is now the most
-common in physics literature) is used and the numbering of references
-will be the order in which they appear in the document. Alternatively, 
-you could use
-a customised `style file' but there is no real need.  The second
-command just inputs your .bib file Note that only the references cited
-in the text will appear in the bibliography so you can have spare
-references in your .bib file.
-
-You use the name you have given to an entry (e.g.
-for the book example above the name is ob:bornwolf)
-to cite the relevant article
-by using the cite command in your \LaTeX\ file e.g. \cite{ob:bornwolf}
-
-\section{Producing your documents using \texttt{pdflatex}}
-
-To use pdflatex your figures need to be in pdf format.  You can convert almost any image file to pdf using \texttt{convert}.  e.g. \texttt{convert myfigure.png myfigure.pdf}.
-
-The first time you should type:
-\begin{verbatim}
-  pdflatex ProjectReport
-  bibtex ProjectReport
-  pdflatex ProjectReport
-  pdflatex ProjectReport
-\end{verbatim} 
-This first time you run\texttt{pdflatex} it will produce a
-\texttt{ProjectReport.aux}.  The \BibTeX\ command reads in the
-bibliography file and makes the files \texttt{ProjectReport.bbl} and
-\texttt{ProjectReport.blg} files.  These files are read in the next
-\texttt{pdflatex} command, but you'll still have ``undefined
-cross-reference'' errors which are sorted out by the last
-\texttt{pdflatex} command.
-
-Subsequently, you should only need to do one (or two)
-\texttt{pdflatex}s, or \texttt{pdfbibtex} followed by
-\texttt{pdflatex} twice if you change any references.
-
-\vspace{5mm} You may also use plain \texttt{latex} instead of
-\texttt{pdflatex}.  This requires you to use postscript graphics
-instead of pdf.
-
-\chapter{Stuff that won't be read by anyone}
-
-Some people include in their thesis a lot of detail, particularly lots
-of tables containing raw results, figures of intermediate results, or
-computer code which no-one will ever read. You should be careful that
-anything like this you include should contain some element of
-uniqueness which justifies its inclusion.
+The mass of the supersymmetric top quark was calculated for the CLIC experiment at $\surd s$ = 3 TeV and for 
+an integrated luminosity $\mathcal{L}_{int}$ = 300 fb$^{-1}$.
+
+Using the Boosted Decision Trees multivariate method of classification it was found to be 
+\begin{equation}
+ m_{\tilde{t}} = 839 \pm 11 \textrm{GeV}/c^{2}
+\end{equation}
+whereas using the Gradient Boosted Decision Trees method of classification it was found to be 
+\begin{equation}
+  m_{\tilde{t}} = 811 \pm 15 \textrm{GeV}/c^{2}
+\end{equation}
+
+Althought the GBDT's at first seem to be better candidate for a more precise mass calculation, the BDT's 
+proved to be the ones that offered a better one. That is because the resulting number of events in the BDT 
+method are more than the ones in GBDT implying that having stronger signal than better separation between 
+signal background is preferable to the case of the mass calculation of the $\tilde{t}$ in CLIC experiment.
+
+\chapter{Further Work}
+
+-isolate leptons
+-further investigation of the contradiccion of bdt gbdt
+-look at other decays of the stop
+-
+?????
 

### 2017-08-09 Tex_Dissertation/MSc_dissertation.tex
endofday

@@
 more than a stranger.
+
+His comments and technical help proved to be valuable, thus I owe a big thank you to Alan Taylor (UoE).
 
@@
 
-Althought the GBDT's at first seem to be better candidate for a more precise mass calculation, the BDT's 
-proved to be the ones that offered a better one. That is because the resulting number of events in the BDT 
+Althought the GBDT's at first seem to be the best candidate for a more precise mass calculation, the BDT's 
+proved to be the ones that offered a better one. That is because the resulting number of signal events in the BDT 
 method are more than the ones in GBDT implying that having stronger signal than better separation between 
-signal background is preferable to the case of the mass calculation of the $\tilde{t}$ in CLIC experiment.
+signal-background is preferable in the case of the mass calculation of the $\tilde{t}$ in CLIC experiment.
 

### 2017-08-10 Tex_Dissertation/MSc_dissertation.tex
welll

@@
 
--interesting---> N of trees
-
-Although, apart from the "cut tunning" issue, the fact that the BDT's performance is superior is is no 
+Another interesting fact is the dependence of the discrimination strength of the classifiers with respect to 
+the number of trees. Before I set the number of trees to be 1000, my initial calculation for the mass 
+was with 200 trees,
+something that yielded an uncertainty of 19 GeV. The reason for that is clear if the following histogram is 
+taken into account:
+
+\begin{figure}[!hb]
+\centering
+  \includegraphics[width=0.6\linewidth]{{images/postbdtcut_200trees}.pdf}
+  \caption{\scriptsize{The signal and the two backgrounds after the BDT cuts for the case of 200 trees.}}
+\end{figure}
+
+If the above histogram is compaired with the corresponding one for 1000 trees (Figure 4.12), then it is clear
+that the SM background has reduced significantly. This is the reason why we get a significance of 11 GeV, i.e.
+8 GeV less.
+
+Although, apart from the "tunning" issues, the fact that the BDT's performance is superior is is no 
 new to the experimental world. From 2005, similar studies were made for the MiniBoone experiment and 
 it was found that BDT's (on Adaboost mode) outperform other methods~\cite{yang2005studies}.
+
+In the following histogram the ROC curve can be seen that
 
@@
 
--isolate leptons
--further investigation of the contradiccion of bdt gbdt
--look at other decays of the stop
--
-?????
+As further work on this project the following can be mentioned:
+
+\begin{itemize}
+ \item As I investigated the following channel
+    \begin{equation}
+      e^{+} e^{+} \rightarrow \tilde{t} \tilde{\bar{t}} \rightarrow t\tilde{\chi}_{1}^{0} \bar{t}\tilde{\chi}_{1}^{0}
+      \rightarrow W^{+}W^{-}b\bar{b} \tilde{\chi}_{1}^{0} \tilde{\chi}_{1}^{0}
+    \end{equation}
+the decay of the W boson can be hadronic or leptonic. By isolating the cases that $W\rightarrow l\nu_{l}$
+,i.e. the hadronic channe, we can possobly achieve even smaller uncertainty in the mass calculation of the top
+squark.
+\item Another possibility is to look also for other decays of the top squarks such as 
+    \begin{equation}
+      e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t \tilde{\chi}_{1}^{0}
+      \chi^{\pm}_{1}b \rightarrow
+      W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}
+    \end{equation}
+
+\item Work also can be done for finding the ideal cut of the BDT classification method as well the most 
+important variables that affect the procedure. One possible way to do such thing is by firstly including
+all the variables in the TMVA and after the training/testing phase to plot the backgroung rejection versus 
+the signal efficiency. Then, repeat the procedure for all the variables besides one and plot again the same 
+graph. That way, step by step, fewer and fewer variables will be taken into account by TMVA and where a huge 
+difference in the plot of backgroung rejection versus signal efficiency is seen, then this will be an 
+indication that this variable is an important one.
+
+\end{itemize}
 

### 2017-08-12 Tex_Dissertation/MSc_dissertation.tex
done1

@@
 
-His comments and technical help proved to be valuable, thus I owe a big thank you to Alan Taylor (UoE).
-
-Additionally I would like to express my gratitude towards the CLICdp team that helped me. Especially
+I also owe my gratitude to Alan Taylor (UoE) for his comments and his technical help throughout this 
+project.
+
+Finally I would like to thank the CLICdp team that helped me. Especially
 to Dr. Philipp Roloff, Dr. Marco Petric, Dr. Ignacio Garcia and Dr. Andre Sailer (all based at CERN).
@@
 Furthermore at the next two stages leading role will play the proposed scenarios for physics BSM with most 
-importantly Supersymmetry at $\surd s$ = 3 TeV and with $\mathcal{L}_{int}$ = 2000 fb$^{-1}$. This  is because CLIC has the potential for direct particle detection up to the 
+importantly Supersymmetry at $\surd s$ = 3 TeV and with $\mathcal{L}_{int}$ = 3000 fb$^{-1}$. This  is because CLIC has the potential for direct particle detection up to the 
 kinematic limit of $\surd s /2$ for pair production but also through indirect detection of observables that are sensitive to BSM
@@
 Given the linear nature of CLIC, there are no energy losses induced by Synchrotron radiation which appears in 
-circular colliders, but due Beamsstrahlung radiation. As the colsliding bunches get closer to the 
+circular colliders, but due Beamsstrahlung radiation. As the colliding bunches get closer to the 
 vertex, the strong electromagnetic fields (up to 10 Tesla) created by the opposing beam, cause deflection
@@
 \hline %inserts double horizontal lines
-$\surd s$ (GeV)  & $\mathcal{L}$   \\ \hline % inserts single horizontal line
-380 & 500 fb$^{-1}$  \\
+$\surd s$ (TeV)  & $\mathcal{L}_{int}$   \\ \hline % inserts single horizontal line
+0.38 & 500 fb$^{-1}$  \\
 1.5 & 1.5 ab$^{-1}$ \\
@@
 mass to the elementary particles (besides photons and gluons which they are protected by the $U(1)$,$SU(3)$
-symmetries respectively)
+unbreakable symmetries respectively)
 via Spontaneous Symmetry Breaking .
@@
 \begin{equation}
- \upsilon \approx 246 \quad GeV
+ \upsilon \approx 246 \quad \textrm{GeV}
 \end{equation}
@@
 \begin{equation}
- M_{H} = \upsilon \sqrt{\frac{\lambda}{2}} 
+ \textrm{M}_{H} = \upsilon \sqrt{\frac{\lambda}{2}} 
 \end{equation}
@@
 regularisation, when $\Lambda \rightarrow \infty$ the renormalisability of the theory assures that there
-is no inconsistency, but if we take into account a scale, for example, for the quantum gravity then $\Lambda \rightarrow 
-M_{P} \approx 1.2\times 10^{19}\quad GeV$ which is the Plank mass, then the additive quantum corrections for the Higgs 
+is no inconsistency, but if we take into account a scale, for example the quantum gravity, then $\Lambda \rightarrow 
+M_{P} \approx 1.2\times 10^{19}\quad \textrm{GeV}$ which is the Plank mass, then the additive quantum corrections for the Higgs 
 mass become too big dragging the value of the Higgs mass up. Because the VEV of the Higgs boson has a fixed 
 phenomenologicaly value, one way to circumvent this problem is by relating bosons with fermions since in the 
-latter, the algebraic terms for their self energies come with a minus sign giving the desired calcelations 
+latter, the algebraic terms for their self energies come with a minus sign giving the desired cancelations 
 without any "fine tuning" from our side. This results into the SUSY theory stabilising the Hierarchy $M_{H}
@@
 something that it is known as Grand Unification. From the point of view of SM, something like that is 
-unable to achieve since two of the couplings decrease with energy (weak and strong coupling) whereas one
+unable to be achieved since two of the couplings decrease with energy (weak and strong coupling) whereas one
 (electromagnetic) increases. In the MSSM, by the inclusion of the sparticles such unification is actually
@@
  \mathcal{M}^{2}_{\tilde{f}} =
-
  \[  
@@
 It is obvious that the $m^{2}_{\tilde{t}_{1}}$ will have the lowest mass, something that makes it the 
-lightest squark.
+lightest squark~\cite{simon2010techniques}.
 
@@
 for the SUSY observables become bigger and bigger as it can be seen in the following figures that summarises
-the latest of them for the stop quark mass at $\surd s$ = 8,13 GeV in proton proton collisions
+the latest of them for the stop quark mass at $\surd s$ = 8/13 GeV in proton proton collisions
 ~\cite{aaboud2016search}:
@@
 I will invedtigate the production of a pair of stop quarks at $\surd s$ = 3 TeV and assumig an  integrated 
-luminosity of $\mathcal{L}_{int}$ = 2000 fb$^{-1}$. The channel of interest is the following:
-
-\begin{equation}
- e^{+} e^{+} \rightarrow \tilde{t} \tilde{\bar{t}} \rightarrow t\tilde{\chi}_{1}^{0} \bar{t}\tilde{\chi}_{1}^{0}
+luminosity of $\mathcal{L}_{int}$ = 3000 fb$^{-1}$. The channel of interest is the following:
+
+\begin{equation}
+ e^{-} e^{+} \rightarrow \tilde{t} \tilde{\bar{t}} \rightarrow t\tilde{\chi}_{1}^{0} \bar{t}\tilde{\chi}_{1}^{0}
  \rightarrow W^{+}W^{-}b\bar{b} \tilde{\chi}_{1}^{0} \tilde{\chi}_{1}^{0}
@@
 
-and for this model the mass of the top squark is $m_{\tilde{t}}$ = 844 GeV whereas the mass of the 
-neutralino is $m_{\tilde{\chi}_{1}^{0}}$. This is not the only possible decay of a top squark but it is the
+and for this model the mass of the top squark is $m_{\tilde{t}}$ = 845 GeV whereas the mass of the 
+neutralino is $m_{\tilde{\chi}_{1}^{0}}$= 357 GeV. This is not the only possible decay of a top squark but it is the
 dominant one. In what follows I show the top three branching ratios of the top squark decay and two
@@
 This involved the vertex finding, the jet clustering, the flavourtagging and the calculation of the $\chi^{2}$
-for each top squark mass.
+for each template of the top squark mass.
 
@@
 existing one LCFIVertex. The important difference between the  two is that LCFIplus employs the vertex finding 
-befere the jet clustering (in comparison to LCFIVertex which follows the exact oposite procedure) with the 
+before the jet clustering (in comparison to LCFIVertex which follows the exact opposite procedure) with the 
 goal to protect the secondadry vertices from breaking up and grouped into different jets~\cite{suehara2016lcfiplus}.
@@
 of this step to be performed before jet clustering, is that hadrons that contain bottom or charm quarks 
-have sizeable lifetimes and they can be measured Inside the detector.
+have sizeable lifetimes and they can be measured inside the detector~\cite{suehara2016lcfiplus}.
 
@@
 serve the need of approaching the initial parton that they originated. Throught the years various algorithms 
-have been developed for the clustering of such objects differing in the way that the approach suchh procedure.
+have been developed for the clustering of such objects differing in the way that they approach such procedure.
 Two of the most famous are the sequential recombination algorithms and cone algorithms. In this projecct I use
@@
 
-For the calculation of the top squark mass I made use of the TMVA package wich is provides a multivariate 
+For the calculation of the top squark mass I made use of the TMVA package which provides a multivariate 
 analysis platform in order (for this project) to make separation between the signal and the background. Two 
-of them were empoyed, used and compaired: the \textit{Boosted Descision Trees} (BDT) and the 
+of them were empoyed, used and compared: the \textit{Boosted Descision Trees} (BDT) and the 
 \textit{Gradient Boosted Descision Trees} (GBDT).
@@
 
-To this end, using the TMVA package in root and trainning 200 trees with the  preselection cuts:
+To this end, using the TMVA package in root and trainning 1000 trees with the  preselection cuts:
 
@@
 created, it applies them to a different sample (test phase). Essentially what TMVA achieves is reducing the 
-multi dimantional phase space of variables into one variable, known as BDT cut.
+multidimensional phase space of variables into one variable, known as BDT cut.
 
@@
 In the histogram below the energy spectrum of the top quark can be seen for the signal events.
-This variable was not given to the TMVA for training and testing. 
-It is clear that the maximum value of the energy is 1200 Tev something that explains why this was also set  
+This variable was given to the TMVA for training and testing but it was not among the important ones. 
+It is clear that the maximum value of the energy is 1.2 Tev something that explains why this was also set  
 as a preselection cut.
@@
 For completenes, the above diagrams depict the SM background efficiency and the SUSY background efficiency.
+
+Note that the descent that manifests in histogram 4.7 in the energy of the top squark is related with the
+effect of Beamsstrahlung radiation. As mentioned in the overview of the experiment, the Beamsstrahlung 
+radiation is energy dependent, being more apparent in higher energies something that is confirmed in the above 
+spectrum.
 
@@
 
-In the following graphs we can see the number of events of the signal and the two backgrounds with respect
+In the following histograms we can see the number of events of the signal and the two backgrounds with respect
 of the $E_{jjj}$ before and after the $cut_{BDT}$. As it can be seen, the Standard Model Background as well as
@@
 
-\begin{table}
+\begin{table}[!hb]
 \centering % used for centering table
@@
 method we calculate the $\chi^{2}$ value for different masses of the top squark, and the minimum of the fitted
-polynomial yields the mass.
+polynomial yields the actuall mass.
 
@@
   \caption{\scriptsize{The $\chi^{2}$ versus the different top squark mass templates. The minimum is at 
-  860 GeV/c$^{2}$.}}
+  839 GeV/c$^{2}$.}}
 \end{figure}
@@
 done 5000 times. The deviation of the Gaussian was chosen to have that value since $\sqrt{n_{data,i}}$
-is the error of each bin content $i$. The result was an uncertainty of the mass 14 GeV.
+is the error of each bin content $i$. The result was an uncertainty of the mass 11 GeV.
 
@@
 imposed the exact same preselection cuts. The purpose of this is to make a comparison of the two methods in 
-the end. For this method 1000 trees were employed.
+the end. For this method 1000 trees were also employed.
 
@@
 Based again, to the graph that has the efficiency vs the $cut_{GBDT}$, the chosen value for the cut was the one
-that maximised the statistical significance $\frac{S}{\sqrt{S+B}}$, where $S$ is the signal and $B$ is the 
+that maximised the statistical significance $\frac{S}{\sqrt{S+B}}$=7.68, where $S$ is the signal and $B$ is the 
 background: $cut_{GBDT}=-0.0606$. It needs to be noted that the statistical significance achieved through
@@
   \caption{\scriptsize{The green line represents the statistical significance $\frac{S}{\sqrt{S+B}}$ where as it can be
-  seen it reaches the greatest value at -0.0606. The cut is also known as descision boundary and defines the
+  seen it reaches the greatest value (7.68) at -0.0606. The cut is also known as descision boundary and defines the
   critical region.}}
@@
 \begin{equation}
- m_{\tilde{t}}=811\quad \textrm{GeV}
+ m_{\tilde{t}}=811\quad \textrm{GeV}/c^{2}
 \end{equation}
@@
 Gaussian of deviation $\sqrt{n_{data}}$ and mean zero, and I repeated the mass calculation. This procedure
-was done 5000 times. The resulting uncertainty was 19 GeV.
+was done 5000 times. The resulting uncertainty was 15 GeV.
 
@@
 
-In this section I am going to compaire the performance as well as the results of the two methods followed in
+In this section I am going to compare the performance as well as the results of the two methods followed in
 this project.
@@
 around the proposed value - in order to extract the lowest uncertainty possible for the mass calculation.
-Furthermore as it can be seen in the above graph, the number of events after the TMVA cut, in the case of 
+Furthermore as it can be seen in the above table, the number of events after the TMVA cut, in the case of 
 GBDT are almost 40 less. Even thought that they sound few, as a fraction they constitute 8$\%$ of the
@@
 number not at all negligible especially when we deal with a few hundreads of events.
-Additionally another interesting thing is the importance of these 40 more events in the case of BDT.
-This is cleat because in the BDT the number of events of SM background ($N_{events}$=528) 
+Additionally another interesting thing is the importance of these 40 more events in the case of BDT 
+(for the mass and the ancertainty calculation).
+This is clear because in the BDT the number of events of SM background ($N_{events}$=528) 
 in total are far more 
 than those in the GBDT method ($N_{events}$=198), and at first sight it would be expected that the GBDT has 
-better potencial than the BDT. The mass and uncertainty measurements proved to be the other way round.
+better potencial than the BDT.
+But the mass and uncertainty measurements proved to be the other way round giving evidence to the fact
+that more signal events have more impact than less background.
 
@@
 
-If the above histogram is compaired with the corresponding one for 1000 trees (Figure 4.12), then it is clear
+If the above histogram is compared with the corresponding one for 1000 trees (Figure 4.12), then it is clear
 that the SM background has reduced significantly. This is the reason why we get a significance of 11 GeV, i.e.
@@
 
-In the following histogram the ROC curve can be seen that
-
 \chapter{Conclusions}
@@
 The mass of the supersymmetric top quark was calculated for the CLIC experiment at $\surd s$ = 3 TeV and for 
-an integrated luminosity $\mathcal{L}_{int}$ = 300 fb$^{-1}$.
+an integrated luminosity $\mathcal{L}_{int}$ = 3000 fb$^{-1}$.
 
@@
     \begin{equation}
-      e^{+} e^{+} \rightarrow \tilde{t} \tilde{\bar{t}} \rightarrow t\tilde{\chi}_{1}^{0} \bar{t}\tilde{\chi}_{1}^{0}
+      e^{-} e^{+} \rightarrow \tilde{t} \tilde{\bar{t}} \rightarrow t\tilde{\chi}_{1}^{0} \bar{t}\tilde{\chi}_{1}^{0}
       \rightarrow W^{+}W^{-}b\bar{b} \tilde{\chi}_{1}^{0} \tilde{\chi}_{1}^{0}
@@
 the decay of the W boson can be hadronic or leptonic. By isolating the cases that $W\rightarrow l\nu_{l}$
-,i.e. the hadronic channe, we can possobly achieve even smaller uncertainty in the mass calculation of the top
+,i.e. the hadronic channe, we can possibly achieve even smaller uncertainty in the mass calculation of the top
 squark.
@@
 all the variables in the TMVA and after the training/testing phase to plot the backgroung rejection versus 
-the signal efficiency. Then, repeat the procedure for all the variables besides one and plot again the same 
+the signal efficiency. Then, repeat the procedure for all the variables excluding one and plot again the same 
 graph. That way, step by step, fewer and fewer variables will be taken into account by TMVA and where a huge 

### 2017-08-15 Tex_Dissertation/MSc_dissertation.tex
introchange

@@
 \begin{center}
-        \huge{\bfseries Calculation of the Supersymmetric top quark mass at CLIC}\\
+        \huge{\bfseries Calculation of the Supersymmetric top quark mass at CLIC $e^{-}e^{+}$ collider.}\\
 \end{center}
@@
         \bigskip
-        \large{August 18, 2017}        % Submission Date
+        \large{August 18, 2017}\\        % Submission Date
+        %\vspace*{3cm}       
+        \bigskip
+        \large{Supervisor: Prof. Victoria Martin}        % Submission Date
+
 \end{center}
@@
 
-On July 2012 the discovery of the Higgs boson was announced at CERN's Large Hadron Collider (LHC).
+On July 2012 the discovery of the Higgs boson was announced at CERN's Large Hadron Collider (LHC)~\cite{aad2012observation}. 
 This marked the begining of a new era for experimental High Energy Physics motivating the design of new 
@@
 
-The main targets of CLIC are dependent of the energy stage.
+The main targets of CLIC are dependent of the energy stage~\cite{clic2016updated}.
 In the first it will focus on prescision standard model physics such as Higgs and Top quark measurements and in the two subsequent, among others, there will be searches
-for new physics~\cite{clic2016updated}.
+for new physics.
 One of the theories that aspires to give solutions to many of the problems of Standard Model is Supersymmetry (SUSY).
 In this theory every particle has a Supersymmetric partner that differs in the spin by $1/2$, thus
-relating bosons with fermions and fermions with bosons.
+relating bosons with fermions and fermions with bosons~\cite{bilal2001introduction}.
 
@@
 Specifically, at $\surd s$ = 380 GeV and with an integrated luminosity of $\mathcal{L}_{int}$ = 500 fb$^{-1}$, 
-prescision measurements can be made in the Higgs and the top quark sector. At this enegy stage the Higgsstrahlung
+prescision measurements can be made in the Higgs and the top quark sector~\cite{clic2016updated}.
+At this enegy stage the Higgsstrahlung
 process ($e^{+}e^{-}\rightarrow ZH$) alongside the $WW$ fusion ($e^{+}e^{-}\rightarrow H\nu_{e}\tilde{\nu}_{e}$) 
-are the dominant and can shed light to properties of the Higgs boson in a model independent way~\cite{clic2016updated}.
-In CLIC there is also a dedicated program for top quark physics, as it is one of the most important particles
+are the dominant and can shed light to properties of the Higgs boson in a model independent way.
+In CLIC there is also a dedicated program for top quark physics. This is because it is one of the most important particles
 in SM because it couples strongest to the Higgs field due to its mass but also it has an important role in 
 many of the BSM scenarios.
-Furthermore at the next two stages leading role will play the proposed scenarios for physics BSM with most 
+Furthermore at the next two stages, leading role will play the proposed scenarios for physics BSM with most 
 importantly Supersymmetry at $\surd s$ = 3 TeV and with $\mathcal{L}_{int}$ = 3000 fb$^{-1}$. This  is because CLIC has the potential for direct particle detection up to the 
-kinematic limit of $\surd s /2$ for pair production but also through indirect detection of observables that are sensitive to BSM
-scenarios through precision measurements and comparison with the SM expectations, 
+kinematic limit of $\surd s /2$ for pair production. Also through indirect detection of observables that are sensitive to BSM
+scenarios, precision measurements can be made, and comparison with the SM expectations can yield unexpected 
+divergencies, 
 taking advantage of the full energy potential.
@@
 \end{tabular}
-\label{table:nonlin} % is used to refer this table in the text
+\label{table:nonlin}% is used to refer this table in the text
+\caption{}
 \end{table}
 
-Furthermore, the experiment has two detector concepts CLIC SiD and CLIC ILD in order to serve the required 
+Furthermore, the experiment has two detector concepts: CLIC SiD and CLIC ILD, in order to serve the required 
 jet energy resolution. The latter has been  developed for the International Linear Collinder but it has been
@@
 
-The model that describes elementary particle physics is the Standar Model. It involves matter  fields (fermions)
+The model that describes elementary particle physics is the Standard Model~\cite{cheng1984gauge}.
+It involves matter  fields (fermions)
 and vector gauge bosons (force carriers) that they stem from the fact that the SM Lagrngian is subject to $SU(3) \otimes 
@@
 Many parts of it are still to be answered or contain significant controversies. One example is the Hierarchy 
-problem. In the electroweak sector of the SM there is a parameter that has the dimensions of energy, the 
-vacum expectation value of the Higgs field which phenomenologicaly is
+problem~\cite{aitchison2005supersymmetry}. 
+In the electroweak sector of the SM there is a parameter that has the dimensions of energy, the 
+vacum expectation value (VEV) of the Higgs field which phenomenologicaly is
 
@@
 regularisation, when $\Lambda \rightarrow \infty$ the renormalisability of the theory assures that there
-is no inconsistency, but if we take into account a scale, for example the quantum gravity, then $\Lambda \rightarrow 
-M_{P} \approx 1.2\times 10^{19}\quad \textrm{GeV}$ which is the Plank mass, then the additive quantum corrections for the Higgs 
+is no inconsistency; but if we take into account a scale such as the quantum gravity, then $\Lambda \rightarrow 
+M_{P} \approx 1.2\times 10^{19}\quad \textrm{GeV}$ which is the Plank mass. In that case 
+the additive quantum corrections for the Higgs 
 mass become too big dragging the value of the Higgs mass up. Because the VEV of the Higgs boson has a fixed 
-phenomenologicaly value, one way to circumvent this problem is by relating bosons with fermions since in the 
+phenomenologicaly value, one way to circumvent this problem is by relating bosons with fermions. 
+This constitutes a solution since in the 
 latter, the algebraic terms for their self energies come with a minus sign giving the desired cancelations 
@@
 \ll M_{P}$ with the constraint that the SUSY particles should be visible at a scale not too much greater 
-than 1-10 TeV~\cite{aitchison2005supersymmetry}.
+than 1-10 TeV.
 
@@
 unable to be achieved since two of the couplings decrease with energy (weak and strong coupling) whereas one
-(electromagnetic) increases. In the MSSM, by the inclusion of the sparticles such unification is actually
-achievable as it can be seen in the following figure:
+(electromagnetic) increases. In the Minimal Supersymmetric Standard Model (MSSM),
+by the inclusion of the supersymmertric particles (sparticles) such unification is actually
+achievable as it can be seen in the following figure
+\textit{(Physics World, October 2014 - IOP publishing)}:
 
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{{images/PWOct14gates-fig2-full}.jpg}
+  \includegraphics[width=0.6\linewidth]{{images/PWOct14gates-fig2-full}.jpg}
   \label{}
@@
 Z Boson & Z & Zino & $\tilde{Z}$ \\
-W Boson & $W^{\pm,0}$ & Wino & $\tilde{W}^{\pm,0}$ \\
-B Boson& B & Bino & $\tilde{B}$ \\ [1ex] % [1ex] adds vertical space
+W Boson & $W^{\pm}$ & Wino & $\tilde{W}^{\pm}$ \\ [1ex] 
+ % [1ex] adds vertical space
 \hline %inserts single line
@@
 \label{table:nonlin} % is used to refer this table in the text
+\caption{}
 \end{table}
@@
 includes the sleptons $\tilde{\ell}^{\pm}$, the sneutrinos $\tilde{\nu}_{l}$, the squarks $\tilde{q}$, the 
-gluinos $\tilde{g}$, two pair of charginos $\tilde{\chi}^{\pm}_{i}$ where $i=1,2$,  four neutralinos 
-$\tilde{\chi}^{0}_{i}$, $i=1,...,4$ and five Higgs bosons $h^{0}$, $H^{0}$, $A^{0}$,$H^{\pm}$.
+gluinos $\tilde{g}$, two pair of charginos $\tilde{\chi}^{\pm}_{i}$ where $i=1,2$ ,  four neutralinos 
+$\tilde{\chi}^{0}_{i}$, $i=1,...,4$ and five Higgs bosons $\tilde{h}^{0}$, $\tilde{H}^{0}$,
+$\tilde{A}^{0}$,$\tilde{H}^{\pm}$.
 
@@
 then it is deduced that SUSY must be a broken symmetry. In order to constitute a solid solution to the 
-Hierarchy problem, then the difference in the masses of the particles and their supersymmetric partners 
+Hierarchy problem, the difference in the masses of the particles and their supersymmetric partners 
 must be of the order of $\mathcal{O}(1  TeV) $~\cite{nagashima2014beyond}.
@@
 In Standard Model, for the Spontaneous Symmetry Breaking one Higgs doublet is needed with 4 degrees of 
-freedom. For the SUSY model on the other hand two such doublets are required with a total of eight 
-degrees of freedom where three of them are absorbed to give mass to the SM particles such as W$^{\pm}$ and Z,
-and the remaining five give rise to five physical Higgs bosons $\tilde{h}$,$\tilde{H}^{\pm}$,$\tilde{A}$,
-$\tilde{H}^{0}$. Those in turn, mix further to become the neutralinos and the charginos : $\tilde{\chi}_{i}^{0}$,
+freedom (complex). For the SUSY model on the other hand, two such doublets are required with a total of eight 
+degrees of freedom. The supersymmertric partners of the SM Higgs, the Higgsinos, mix with the Winos 
+$\tilde{W}^{\pm}$ and the 
+Binos $\tilde{B}$ in order to form the neutralinos $\tilde{\chi}_{i}^{0}$ and the charginos 
 $\tilde{\chi}_{i}^{\pm}$.
 
+%where three of them are absorbed to give mass to the SM particles such as W$^{\pm}$ and Z,
+%and the remaining five give rise to five physical Higgs bosons $\tilde{h}$,$\tilde{H}^{\pm}$,$\tilde{A}$,
+%$\tilde{H}^{0}$. Those in turn, mix further to become the neutralinos and the charginos : $\tilde{\chi}_{i}^{0}$,
+%$\tilde{\chi}_{i}^{\pm}$.
+
 It is known that within the SM the fermions carry chirality denoted by L or R whether they are left or right 
-respectively, according to the way they transform under the symmetry group $SU(2) \otimes U(1)$. Thus given 
+respectively, according to the way they transform under the symmetry group $SL(2,\mathbb{C})$. Thus given 
 the SUSY relation of fermions-bosons that means that the sfermions  (bosonic superpartners), come into 
@@
 of the mass matrix. This mixing is expected to be strong for third generation sfermions since the Yukawa 
-couplings can be large, more precisely in our case the stop quark mixing effects can be large because
+couplings can be large. More precisely in our case the stop quark mixing effects can be large because
 of the large mass of the top quark.
@@
 where the $M^{2}_{\tilde{f}_{L}}$ are terms that depend on the mass of the quark, the charge and the third 
-component of the weak isospin. The off diagonal elements $\alpha_{f}$ are dependent on the soft SUSY breaking
+component of the weak isospin~\cite{simon2010techniques}.
+The off-diagonal elements $\alpha_{f}$, are dependent on the soft SUSY breaking
 trilinear scalar coupling parameters.
@@
 due to the large top quark mass. By computing the eigenvalues of the previous matrix and for the right
-flavour we obtain:
+flavour, we obtain:
 
@@
 It is obvious that the $m^{2}_{\tilde{t}_{1}}$ will have the lowest mass, something that makes it the 
-lightest squark~\cite{simon2010techniques}.
+lightest squark.
 
@@
  The search for indications for Supersymmetry is not new as LHC has been optimized and focused among other
- to the direct or indirect detection of sparticles. The majority of the cases that have been studied, 
- consider as main decay channel of the sparticles the following:
+ to the direct or indirect detection of sparticles~\cite{chatrchyan2011search}.
+The majority of the cases that have been studied, consider as main decay channel of the sparticles 
+the following:
 
@@
 So far thought no indication of SUSY has been found in LHC but through each analysis the exclusion limits 
-for the SUSY observables become bigger and bigger as it can be seen in the following figures that summarises
+for the SUSY observables become bigger and bigger as it can be seen in the figure 3.1 that summarises
 the latest of them for the stop quark mass at $\surd s$ = 8/13 GeV in proton proton collisions
-~\cite{aaboud2016search}:
-
-\begin{figure}[h!]
+~\cite{aaboud2016search}.
+
+\begin{figure}[!hb]
   \centering
@@
   \label{fig2.15}
-\end{figure}
-
-Whereas in the following figure there are the exclusion limits in ATLAS for p-p collisions at 13 TeV for the
-channel invastiged in this project
+  \caption{\scriptsize{Mass exclusion limits at stop-neutralino plane.}}
+\end{figure}
+
+Whereas in the figure 3.2 there are the latest exclusion limits in ATLAS for p-p collisions at 13 TeV in the gluino-
+stop plane.
 
@@
   \centering
-  \includegraphics[width=0.6\linewidth, scale=5]{{images/fig_08}.png}
+  \includegraphics[width=0.6\linewidth, scale=5]{{images/gluino}.png}
   \label{}
+  \caption{\scriptsize{Mass exclusion limits at stop-gluino plane.}}
 \end{figure}

### 2017-08-15 Tex_Dissertation/MSc_dissertation.tex
introchange

@@
   \label{fig2.15}
-  \caption{\scriptsize{Mass exclusion limits at stop-neutralino plane.}}
+  \caption{\scriptsize{Mass exclusion limits at stop-neutralino plane (combined summary plot from ATLAS 
+  twiki).}}
 \end{figure}
@@
   \label{}
-  \caption{\scriptsize{Mass exclusion limits at stop-gluino plane.}}
+  \caption{\scriptsize{Mass exclusion limits at stop-gluino plane~\cite{atlassearch}.}}
 \end{figure}

### 2017-08-16 Tex_Dissertation/MSc_dissertation.tex
started

@@
 \begin{center}
-        \huge{\bfseries Calculation of the Supersymmetric top quark mass at CLIC $e^{-}e^{+}$ collider.}\\
+        \huge{\bfseries Measurement of the Supersymmetric top quark mass at CLIC $e^{-}e^{+}$ collider.}\\
 \end{center}
@@
 Finally I would like to thank the CLICdp team that helped me. Especially
-to Dr. Philipp Roloff, Dr. Marco Petric, Dr. Ignacio Garcia and Dr. Andre Sailer (all based at CERN).
+Dr. Philipp Roloff, Dr. Marco Petric, Dr. Ignacio Garcia and Dr. Andre Sailer (all based at CERN).
 
@@
 
-On July 2012 the discovery of the Higgs boson was announced at CERN's Large Hadron Collider (LHC)~\cite{aad2012observation}. 
+On July 2012 the discovery of the Higgs boson was announced at CERN's Large Hadron Collider (LHC)~\cite{aad2012observation}
+~\cite{higgs1966spontaneous}. 
 This marked the begining of a new era for experimental High Energy Physics motivating the design of new 
@@
 It is designed for a staging scenario of three main centre of mass energies at $\surd{s}$ = 380 GeV, $\surd{s}$ = 1.5 TeV
-and $\surd{s}$ = 3 TeV targeting optimal physics output based on the current landscape.
+and $\surd{s}$ = 3 TeV targeting optimal physics output based on the current landscape~\cite{clic2016updated}. 
 The main difference of CLIC with LHC is that in the latter, protons collide which are non fundamental particles as they consist of quarks and 
@@
 On the other hand, CLIC is designed to invastigate the interactions of elementary particles, an important advantage since initial states of the colliding particles is known.
-In advance, LHC suffers from energy loss due to
+In addition, LHC suffers from energy loss due to
 Synchrotron radiation since protons are accelerated in a 27 km circular accelerator whereas CLIC, being linear does not.
@@
 The main targets of CLIC are dependent of the energy stage~\cite{clic2016updated}.
-In the first it will focus on prescision standard model physics such as Higgs and Top quark measurements and in the two subsequent, among others, there will be searches
+In the first it will focus on prescision standard model physics such as Higgs and top quark measurements and in the two subsequent, among others, there will be searches
 for new physics.
@@
 
-In the Minimal Supersymmetric Standard Model, the top squarks $\tilde{t}$ decay almost all the times into a top quark $t$
-and a dark matter candidate, the neutralino $\tilde{\chi}_{1}^{0}$. In this project I will use Multivariate Analisis
-to discriminate the best it can be achieved between signal and background with the goal to measure the top squark
+In the Minimal Supersymmetric Standard Model, the top squarks $\tilde{t}$ can decay into a top quark $t$
+and a dark matter candidate, the neutralino $\tilde{\chi}_{1}^{0}$. In this project I will use multivariate analysis
+to discriminat between signal and background with the goal to measure the top squark
 mass at $\surd{s}$ = 3 TeV in the CLIC accelerator environment.
@@
 many of the BSM scenarios.
-Furthermore at the next two stages, leading role will play the proposed scenarios for physics BSM with most 
+Furthermore at the next two energy stages, investigations will be done with respect to 
+proposed scenarios for physics BSM with most 
 importantly Supersymmetry at $\surd s$ = 3 TeV and with $\mathcal{L}_{int}$ = 3000 fb$^{-1}$. This  is because CLIC has the potential for direct particle detection up to the 
@@
 of the partices trajectories resulting to emit Synchrotron radiation. The effect is energy-dependent with huge
-impact at higher energies~\cite{bonvicini1989first} as it can be seen in the following 
-image~\cite{abramowicz2017higgs}.
+impact at higher energies~\cite{bonvicini1989first} as it can be seen in figure 
+2.1~\cite{abramowicz2017higgs}.
 
@@
 
-Furthermore, the experiment has two detector concepts: CLIC SiD and CLIC ILD, in order to serve the required 
-jet energy resolution. The latter has been  developed for the International Linear Collinder but it has been
+Furthermore, the experiment has two detector concepts: CLIC SiD and CLIC ILD. 
+Both have been  developed for the International Linear Collinder but it has been
 adapted according to the needs of CLIC. Both detectors have strong central solenoid magnets creating an axial 
@@
 
-The model that describes elementary particle physics is the Standard Model~\cite{cheng1984gauge}.
+The model that describes elementary particle physics is the Standard Model~\cite{cheng1984gauge}~\cite{weinberg1967model}.
 It involves matter fields (fermions)
-and vector gauge bosons (force carriers) that they stem from the fact that the SM Lagrngian is subject to $SU(3) \otimes 
+and vector gauge bosons (force carriers) that they stem from the fact that the SM Lagrangian is subject to $SU(3) \otimes 
 SU(2) \otimes U(1)$ symmetries. An important part of this theory is the existence of the Higgs field which appeared
 during the unification of the electromagnetic and the weak force. It is known for the fact that it "gives"
-mass to the elementary particles (besides photons and gluons which they are protected by the $U(1)$,$SU(3)$
+mass to the elementary particles (besides photons and gluons which they are protected by the $U(1)$, $SU(3)$
 unbreakable symmetries respectively)
-via Spontaneous Symmetry Breaking .
+via Spontaneous Symmetry Breaking.
 
@@
 \begin{equation}
- \int_{}^{\Lambda} d^{4}k \quad f(k,external\quad momenta)
+ \int_{}^{\Lambda} d^{4}k \quad f(k,\textrm{external momenta})
 \end{equation}
@@
 is no inconsistency; but if we take into account a scale such as the quantum gravity, then $\Lambda \rightarrow 
-M_{P} \approx 1.2\times 10^{19}\quad \textrm{GeV}$ which is the Plank mass. In that case 
+M_{P} \approx 1.2\times 10^{19} \textrm{GeV}$ which is the Plank mass. In that case 
 the additive quantum corrections for the Higgs 
@@
 
-The framework of this project is the Minimal Supersymmetric Standard Model which besides the SM particles 
-includes the sleptons $\tilde{\ell}^{\pm}$, the sneutrinos $\tilde{\nu}_{l}$, the squarks $\tilde{q}$, the 
-gluinos $\tilde{g}$, two pair of charginos $\tilde{\chi}^{\pm}_{i}$ where $i=1,2$ ,  four neutralinos 
-$\tilde{\chi}^{0}_{i}$, $i=1,...,4$ and five Higgs bosons $\tilde{h}^{0}$, $\tilde{H}^{0}$,
-$\tilde{A}^{0}$,$\tilde{H}^{\pm}$.
+The framework of this project is the Minimal Supersymmetric Standard Model.
 
@@
 
+The MSSM includes the sleptons $\tilde{\ell}^{\pm}$, the sneutrinos $\tilde{\nu}_{l}$, the squarks $\tilde{q}$, the 
+gluinos $\tilde{g}$, two pair of charginos $\tilde{\chi}^{\pm}_{i}$ where $i=1,2$ ,  four neutralinos 
+$\tilde{\chi}^{0}_{i}$, $i=1,...,4$ and five Higgsinos $\tilde{h}^{0}$, $\tilde{H}^{0}$,
+$\tilde{A}^{0}$,$\tilde{H}^{\pm}$.
 In Standard Model, for the Spontaneous Symmetry Breaking one Higgs doublet is needed with 4 degrees of 
@@
 the SUSY relation of fermions-bosons that means that the sfermions  (bosonic superpartners), come into 
-doublets of the form $(f_{i},\tilde{f}_{i})$, where i=L,R. The sfermions mix further to make the eigenstates
+doublets of the form (SM particle, SUSY partner), i.e.: $(f_{i},\tilde{f}_{i})$, where i=L,R. 
+The sfermions mix further to make the eigenstates
 of the mass matrix. This mixing is expected to be strong for third generation sfermions since the Yukawa 
-couplings can be large. More precisely in our case the stop quark mixing effects can be large because
+couplings can be large. More precisely in our case the top squark mixing effects can be large because
 of the large mass of the top quark.
@@
 
-In this project I will focous on the top squarks  where the mixing   $\tilde{t}_{R}-\tilde{t}_{L}$ is important
+In this project I will focus on the top squarks  where the mixing   $\tilde{t}_{R}-\tilde{t}_{L}$ is important
 due to the large top quark mass. By computing the eigenvalues of the previous matrix and for the right
@@
 
-It is obvious that the $m^{2}_{\tilde{t}_{1}}$ will have the lowest mass, something that makes it the 
-lightest squark.
+It is obvious that the $m^{2}_{\tilde{t}_{1}}$ will have the lowest mass, something that makes it
+probably the lightest squark.
 
@@
  to the direct or indirect detection of sparticles~\cite{chatrchyan2011search}.
-The majority of the cases that have been studied, consider as main decay channel of the sparticles 
+The majority of the cases that have been studied, consider as main decay channel of the squarks 
 the following:
@@
 So far thought no indication of SUSY has been found in LHC but through each analysis the exclusion limits 
-for the SUSY observables become bigger and bigger as it can be seen in the figure 3.1 that summarises
-the latest of them for the stop quark mass at $\surd s$ = 8/13 GeV in proton proton collisions
+for the SUSY observables become bigger and bigger. This can be seen in the figure 3.1 
+that summarises
+the latest exclusion limits for the top squark mass at $\surd s$ = 8/13 GeV in proton proton collisions
 ~\cite{aaboud2016search}.
-
-\begin{figure}[!hb]
-  \centering
-  \includegraphics[width=0.7\linewidth]{{images/ATLAS_SUSY_Stop_tLSP}.png}
+Whereas in the figure 3.2 are the latest exclusion limits in ATLAS for p-p collisions at 13 TeV in the gluino -
+stop plane.
+
+\begin{figure}[!h]
+  \centering
+  \includegraphics[width=0.6\linewidth]{{images/ATLAS_SUSY_Stop_tLSP}.png}
   \label{fig2.15}
@@
 
-Whereas in the figure 3.2 there are the latest exclusion limits in ATLAS for p-p collisions at 13 TeV in the gluino-
-stop plane.
-
-\begin{figure}[ht!]
+%Whereas in the figure 3.2 there are the latest exclusion limits in ATLAS for p-p collisions at 13 TeV in the gluino-
+%stop plane.
+
+\begin{figure}[h!]
   \centering
@@
 In this chapter I will describe the exact conditions and methods that were followed in this project for the 
-calculation of the stop quark mass at CLIC Conceptual experiment.
-
-I will invedtigate the production of a pair of stop quarks at $\surd s$ = 3 TeV and assumig an  integrated 
+measurement of the stop quark mass at the CLIC Conceptual experiment.
+
+I investigate the production of a pair of top squarks at $\surd s$ = 3 TeV and assuming an  integrated 
 luminosity of $\mathcal{L}_{int}$ = 3000 fb$^{-1}$. The channel of interest is the following:
@@
 
-and for this model the mass of the top squark is $m_{\tilde{t}}$ = 845 GeV whereas the mass of the 
-neutralino is $m_{\tilde{\chi}_{1}^{0}}$= 357 GeV. This is not the only possible decay of a top squark but it is the
+and for this model the mass of the top squark is $m_{\tilde{t}}$ = 845 GeV (denoted as $M_{nom}$ later
+in the text)
+whereas the mass of the 
+lightest neutralino is $m_{\tilde{\chi}_{1}^{0}}$= 357 GeV. This is not the only possible decay of a top 
+squark but it is the
 dominant one. In what follows I show the top three branching ratios of the top squark decay and two
@@
 
-As also the branching ratios for the decay of the W boson to either in a hadronic final state or in
+Also, the branching ratios for the decay of the W boson to either a hadronic final state or 
 a leptonic one are:
@@
  \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t \tilde{\chi}_{1}^{0}
- \chi^{\pm}_{1}b \rightarrow
+ \tilde{\chi}^{\pm}_{1}b \rightarrow
  W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}$ \quad (35.8\%)
@@
  \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t\bar{t} \tilde{\chi}_{1}^{0}
- \chi^{0}_{2} \rightarrow
+ \tilde{\chi}^{0}_{2} \rightarrow
  W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}h$ \quad (13.7\%)
 
- \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow b\bar{b} \chi_{1}^{+}
- \chi^{-}_{1} \rightarrow
+ \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow b\bar{b} \tilde{\chi}_{1}^{+}
+ \tilde{\chi}^{-}_{1} \rightarrow
  W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}$ \quad (11.6\%)
@@
  \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t \tilde{\chi}_{2}^{0}
- \chi^{\pm}_{1}b \rightarrow
+ \tilde{\chi}^{\pm}_{1}b \rightarrow
  W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}h$ \quad (9\%)
@@
 
-\section{Calculation of SUSY particle masses}
+\section{Measurement of SUSY particle masses}
 
@@
 The main topologies that are considered are those that the gluino is heavier than the squarks and thus the 
-dominant decaying channel is:
+dominant production and decay channel is:
 
@@
 
-This technique has been developed initially for LHC experiment where the p-p collision energy is not known.
+This technique has been developed initially for LHC experiment where the energy that is used
+to make the squark - antisquark pair is not known.
 The calculation was achieved by creating the variable $M_{C}$ which is related to the standard 
@@
 \begin{equation}
- M_{C}^{2}=2(E_{q,1}E_{q,2}+\vec{p}_{q,1}\vec{p}_{q,2})
+ M_{C}^{2}=2(E_{q,1}E_{q,2}+\vec{p}_{q,1}\cdot \vec{p}_{q,2})
 \end{equation}
@@
 the Beamstrahlung can distort it significantly resulting to even bigger uncertainties. Note that this method 
-assumes that the mass of the neutralino is known and that the quark is massless.
+assumes that the mass of the neutralino is known and that the quark is massless and therefore
+unsuitable for the mass measurement of the top squark.
 
@@
 In this chapter I describe the procedure that I followed until the calculation of the top squark mass. 
-This involved the vertex finding, the jet clustering, the flavourtagging and the calculation of the $\chi^{2}$
+This involved vertex finding, jet clustering, flavour tagging and the calculation of the $\chi^{2}$
 for each template of the top squark mass.
@@
 \subsection{Vertex Finding}
+
+The point that particles collide in a collider experiment is called primary vertex or interaction 
+point (IP). After that 
+collision, it is possible that some of the particles will decay further away from the IP. The point 
+that this decay takes place is called secondary vertex. Every analysis that involves jet clustering
+procedure (and not only) has as starting point the vertex finding. This involves an algorithm
 

### 2017-08-16 Tex_Dissertation/MSc_dissertation.tex
alm

@@
 
+ In this project I investigate the first channel with the W boson decaying into hadrons. This results
+ into having 6 jets in the final products. The channel explicitly is:
+
+ $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t \bar{t}\tilde{\chi}_{1}^{0}
+ \tilde{\chi}^{0}_{1} \rightarrow
+ W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0} \rightarrow 
+ q \bar{q} q \bar{q} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}$
+
 \newpage
@@
 The point that particles collide in a collider experiment is called primary vertex or interaction 
-point (IP). After that 
+point (IP). After the 
 collision, it is possible that some of the particles will decay further away from the IP. The point 
 that this decay takes place is called secondary vertex. Every analysis that involves jet clustering
-procedure (and not only) has as starting point the vertex finding. This involves an algorithm
+procedure (and not only) has as starting point the vertex finding. This involves an algorithm that 
+classifies the tracks of the particles into vertex candidates (vertex finding) and "passes it on"
+to the vertex fitting  algorithm. In turn, the latter, takes the vertex candidates and outputs a
+list of vertices with their position using the $\chi^{2}$ or a related statistical method. 
+Additionally, it yields a set of parameters that are related to each particular production point.
+
+The reasons of why an accurate vertex finding is important are:
+
+\begin{itemize}
+ \item Information can be exctracted about short lived particles such as their decay length.
+ \item There can be improvement with respect to momentum estimate of the particles involved in each 
+ vertex.
+ \item Reconstruction can be achieved for short lived particles by its decay products by fitting them
+ into one particular vertex.
+\end{itemize}
 
@@
 before the jet clustering (in comparison to LCFIVertex which follows the exact opposite procedure) with the 
-goal to protect the secondadry vertices from breaking up and grouped into different jets~\cite{suehara2016lcfiplus}.
-This is an important step towards better performance since the Bottom jets can be identified from their 
+goal to protect the secondary vertices from breaking up and grouped into different jets~\cite{suehara2016lcfiplus}.
+This is an important step towards better performance since the bottom jets can be identified from their 
 sufficiently large distance between the primary vertex and their decay vertex. Additionally, the importance
@@
 the a sequential recombination algorithm, the $k_{t}$ algorithm which is a longitudinaly invariant algorithm
-firstly designed for hadron colliders.
+firstly designed for hadron colliders~\cite{catani1993longitudinally}~\cite{ellis1993successive}.
 
@@
 $\Delta R^{2}_{ij}=(y_{i}-y_{j})^{2}+(\phi_{i}-\phi_{j})^{2}$ with $y$ being the rapitdity, $\phi$ being
-the azimuth angle and R the jet radius fixed in this project as $R=0.7$.
+the azimuth angle and $R$ the jet radius fixed in this project as $R=0.7$.
 
@@
 "merges" the $i,j$ into a single object with momentum $p_{i}+p_{j}$. This procedure is repeated until the quantity
-$d_{ij}$ is above some threshold and all the particles that are left are the event's jet
-~\cite{cacciari2012fastjet}.
-
+$d_{ij}$ is above some threshold and all the particles that are left are the event's jet~\cite{cacciari2012fastjet}.
+
+For this project the jet clustering procedure is stoped when the number of jets reaches the number 
+6, since in the final products there are 6 jets (see section 4.1).
 \subsection{Flavour Tagging}
 
-Flavour Tagging is the procedure in which a pseudoprobability is assigned to each jet regarding the parton
-that the jet originates from. In this project, there are six jets in the final products four of them 
+Flavour Tagging is the procedure in which a pseudoprobability is assigned to each jet regarding the
+flavour of the parton
+that the jet originates from. In this project, there are six jets in the final products two of them 
 originating from b quarks.
 
-The flavour tagging algorithm that was used belonged in the LCFIplus package~\cite{suehara2016lcfiplus}.
+The flavour tagging algorithm belongs in the LCFIplus package~\cite{suehara2016lcfiplus}.
 It  makes use of the TMVA package which in turn uses multivariate classifiers. A set of input variables are 
-defined for each jet and they are passed to the Gradien Boosted Descision Trees (a certain type of classifiers)
+defined for each jet and they are passed to the Gradient Boosted Descision Trees (a certain type of classifiers)
 which they are trained and then applied to the jets of the physical process. Those input variables are

### 2017-08-16 Tex_Dissertation/MSc_dissertation.tex
doneuntilp15

@@
 analysis platform in order (for this project) to make separation between the signal and the background. Two 
-of them were empoyed, used and compared: the \textit{Boosted Descision Trees} (BDT) and the 
+of them were employed, used and compared: the \textit{Boosted Descision Trees} (BDT) and the 
 \textit{Gradient Boosted Descision Trees} (GBDT).
@@
 momenta, missing energy, etc. Then TMVA sorts all events by each variable and we choose the one that gives the
-best separation between signal and background. This is how the first node is made called root. Then, in the two branches 
+best separation between signal and background. This is how the first node is made called root node. 
+Then, in the two branches 
 that are made we repeat this procedure applying the best cut on each node until the splitting stops based on 
-some criterion. That is how the terminal node is reached which is called leaf~\cite{hoecker2007tmva}.
+some criterion. That is how the terminal node is reached which is called a leaf~\cite{hoecker2007tmva}.
+This results into a descision tree where all nodes, from root to leaf node, separate (cut) the input
+data into signal and background based on some criteria.
+
+The "learning" phase where the nodes are created is called training phase. After this, where the 
+nodes have been created, they are tested with a (not necessarily) new  data set in order to 
+check their efficiency. This is called the testing phase.
 
@@
 
-A way to circumvent this problem is to employ many different trees whose depth is small. They are called
+A way to circumvent this problem is to employ many different trees whose depth (number of nodes
+of each tree) is small. 
+They are called
 weak learners. The classification of the event comes from the majority vote of these weak learners (boosting).
-It is important to be noted that each tree is trainned with the same sample of input variables. That way not 
+It is important to be noted that each tree is trained with the same sample of input variables. That way not 
 only we reach better results in the possible presence of statistical fluctuations but we also avoid the 

### 2017-08-17 Tex_Dissertation/MSc_dissertation.tex
morning

@@
 
-In the physical case that I examine what will later be denoted as SUSY signal: corresponding to the 
-top squarks, SUSY and SM background: corresponding to any physical process that immitates the one under 
-consideration.
-
-To this end, using the TMVA package in root and trainning 1000 trees with the  preselection cuts:
+The products of the particle collision can be separated as signal and background.
+The channel of interest is denoted as SUSY signal, i.e.:
+
+ $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t \bar{t}\tilde{\chi}_{1}^{0}
+ \tilde{\chi}^{0}_{1} \rightarrow
+ W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0} \rightarrow 
+ q \bar{q} q \bar{q} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}$
+
+The SUSY background is any other SUSY process that involves top squark pair production but the final products 
+are not the ones of interest, and the SM background which does not involve any supersymmetric process.
+
+Before the training and testing phase it is possible to impose some constraints to the input kinematic 
+variables. They are called preselection cuts.
+
+% In the physical case that I examine what will later be denoted as SUSY signal: corresponding to the 
+% top squarks, SUSY and SM background: corresponding to any physical process that immitates the one under 
+% consideration.
+
+To this end, using the TMVA package in ROOT and trainning 1000 trees with the  preselection cuts:
 
@@
 where $E_{visible}$ is the total energy of the jets and $E_{top,i}$ is the energy of the $i^{th}$ top quark.
-99$\%$ of the signal events passed the cut whereas for the background 70$\%$.
-
-In what follows I enumerate the input variables in the TMVA that they were used for trainning and testing 
-the classifiers. It is important to notice that the sample with which the BDT's was trainned and tested were
-different.
+99$\%$ of the signal events pass the preselection cuts whereas for the background 70$\%$.
+
+In what follows I enumerate the input variables in the TMVA that they are used for trainning and testing 
+the classifiers. It is important to notice that the sample with which the BDT's was trainned and tested are
+different. Some of those variables can be seen in figures 4.3 - 4.6.
 

### 2017-08-17 Tex_Dissertation/MSc_dissertation.tex
before

@@
 \begin{enumerate}
- \item The invariant masses of the top quarks
- \item The invariant masses of the W bosons
- \item The missing transverse momentum  $p_{T}$
+ \item The the reconstructed masses of the top quark candidates
+ \item The reconstructed masses of the W boson candidates
+ \item The missing transverse momentum  $p_{T}$ (transversity with respect to the beam line)
  \item The $\Delta \phi$ angle between the $t\bar{}t$ quarks
  \item The $\Delta R$  between the W candidates and the b jets
- \item The $cos\theta_{top}$. We expect the top quarks created by purely SM processes to be more boosted 
- than the ones that involved SUSY processes.
+ \item The $\cos\theta_{top}$. We expect the top quarks created by purely SM processes to be more boosted 
+ than the ones that involved SUSY processes
  \item Thrust: 
@@
  \end{equation}
-	where $\hat{n}$ is the unitary vector that maximises the ratio of the sums. The sums run over all the
-	particles that emerge from the collision.
+	where $\hat{n}$ is the unit vector that maximises the ratio of the sums. The sums run over all the
+	particles that emerge from the collision
 
@@
   \item Aplanarity (defined in~\cite{chen2012new})
-  \item The number of particles
+  \item The number of particles detected
   \item $y_{3,4},y_{4,5},y_{5,6},y_{6,7},y_{7,8}$: The jet transition values defined from the following 
@@
   \begin{equation}
-   y_{i,j}=min(E_{i}^{2},E_{j}^{2})\frac{1-(cos\theta_{i}-cos\theta_{j})}{s}
-  \end{equation}
-  where i,j jets are chosen such that y gets the minimum value. 
+   y_{i,j}=\min(E_{i}^{2},E_{j}^{2})\frac{1-(\cos\theta_{i}-\cos\theta_{j})}{s}
+  \end{equation}
+  where $i,j$ jets are chosen such that $y$ gets the minimum value 
 \end{enumerate}
@@
 
-The TMVA trains the classifiers with respect to the input variables and then with the weight files that it has
-created, it applies them to a different sample (test phase). Essentially what TMVA achieves is reducing the 
+The TMVA trains the classifiers with respect to the input variables, listed above, 
+on generated samples of the signal and backgrounds. The TMVA creates "weight files" which in turn are 
+applied to statistically independent samples of the signal and background processes (test phase). 
+Essentially what TMVA achieves is reducing the 
 multidimensional phase space of variables into one variable, known as BDT cut.
 
-According to the following graph, the value of the BDT cut that was chosen is $cut_{BDT}=-0.036$ due to the 
-fact that it has the maximum statistical significance $\frac{S}{\sqrt{S+B}}$=5.68, where S is the
-number of signal events and B is the number of background events.
+As shown in the following graph, the value of the BDT cut that was chosen is $cut_{BDT}=-0.036$ due to the 
+fact that it has the maximum statistical significance $\frac{S}{\sqrt{S+B}}$=5.68, where $S$ is the
+number of signal events and $B$ is the number of background events.
 
 \begin{figure}[ht!]
+ \centering
   \includegraphics[width=0.6\linewidth]{{images/cutefficiences_1000trees2}.pdf}
   \caption{\scriptsize{The green line represents the statistical significance $\frac{S}{\sqrt{S+B}}$ where as it can be
-  seen it reaches the greatest value at -0.0238. The cut is also known as descision boundary and defines the
+  seen it reaches the greatest value at $\num{-0.0238}$. 
+  The cut is also known as descision boundary and defines the
   critical region.}}
@@
  \item missing $p_{T}$ 
- \item $\Delta \phi$
+ \item $\Delta \phi$ as the angle between the $t\bar{t}$
  \item $cos\theta_{top}$
@@
 This variable was given to the TMVA for training and testing but it was not among the important ones. 
-It is clear that the maximum value of the energy is 1.2 Tev something that explains why this was also set  
+It is clear that the maximum value of the energy is 1.2 TeV something that explains why this was also set  
 as a preselection cut.
@@
   \includegraphics[width=0.7\linewidth]{{images/E_jjj}.pdf}
-  \caption{\scriptsize{The energy of the top quark. For higher energies there are less entries per bin, something that
-  is connected with the effect of Beamsstrahlung radiadion that is manifested mainly in higher energies.}}
+  \caption{\scriptsize{The energy of the reconstructed top quark candidate.}}
 \end{figure}
@@
   \includegraphics[width=0.7\linewidth]{{images/ratio_plot_witherrors}.pdf}
-  \caption{\scriptsize{}}
+  \caption{\scriptsize{The signal efficiency with the associated errors.}}
 \end{figure}
@@
 
-Note that the descent that manifests in histogram 4.7 in the energy of the top squark is related with the
-effect of Beamsstrahlung radiation. As mentioned in the overview of the experiment, the Beamsstrahlung 
-radiation is energy dependent, being more apparent in higher energies something that is confirmed in the above 
-spectrum.
+% Note that the descent that manifests in histogram 4.7 in the energy of the top squark is related with the
+% effect of Beamsstrahlung radiation. As mentioned in the overview of the experiment, the Beamsstrahlung 
+% radiation is energy dependent, being more apparent in higher energies something that is confirmed in the above 
+% spectrum.
 
@@
 
-\subsubsection{Mass Calculation Results}
+\subsubsection{Mass Measurements Results}
 
@@
 and $n_{template}$ are the number of events for each different template, while the sum runs over all the bins
-of the histogram. A $\chi^{2}$ was calculated for each different template, summarised in the table below.
+$i$ of the histogram. A $\chi^{2}$ was calculated for each different template, summarised in the table below.
 
@@
 $M_{template}$ 		   & $\sigma$ (fb)   \\ \hline % inserts single horizontal line
-$M_{nom}$ -200 GeV         &   2.8   \\
-$M_{nom}$ -100 GeV         &   2.2   \\
-$M_{nom}$ -50  GeV         &   1.9   \\  
+$M_{nom}   \num{-200}$ GeV         &   2.8   \\
+$M_{nom}   \num{-100}$ GeV         &   2.2   \\
+$M_{nom}   \num{-50}$  GeV         &   1.9   \\  
 $M_{nom}$        	   &  1.65   \\
-$M_{nom}$ +50  GeV	   &   1.4   \\
-$M_{nom}$ +100 GeV	   &   1.2   \\
-$M_{nom}$ +200 GeV	   &   0.8   \\
+$M_{nom}   \num{+50}$  GeV	   &   1.4   \\
+$M_{nom}  \num{+100}$  GeV	   &   1.2   \\
+$M_{nom}  \num{+200}$  GeV	   &   0.8   \\
 
@@
 
-The mass was found  to be $m_{\tilde{t}}$ = 839 GeV.
+The mass was found  to be $m_{\tilde{t}}$ = 839 GeV compaired to the mass of the Monte Carlo sample which 
+is $m_{\tilde{t}}$ = 845 GeV/$c^{2}$.
 
@@
   \includegraphics[width=0.7\linewidth]{{images/toyMC_intlumi3000}.pdf}
-  \caption{\scriptsize{Toy Monte carlo method that yielded an uncertainty of 11 GeV.}}
+  \caption{\scriptsize{The mass result after 5000 different measurements. 
+ A toy Monte Carlo method was used that yielded an uncertainty of 11 GeV.}}
 \end{figure}
@@
 
-Although the nominal mass is $M_{nom}$= 845 GeV/$c^{2}$, my calculation is one sigma  inside this range,
+The nominal mass is $M_{nom}$= 845 GeV/$c^{2}$, my measurement is one sigma  inside this range,
 taking into account the aforementioned uncertainty at CLIC for integrated luminosity 
@@
 
-Again like all the boosting methods, it combines a set of weak learners (for BDT it was the number of trees).
+Again like all the boosting methods, it combines a set of weak learners which is defined to be the trees that
+are "short", i.e. that they have small number of nodes.
 In the first phase -training phase- a rough approximation for the prediction model is made. Subsequently, the 
@@
 background: $cut_{GBDT}=-0.0606$. It needs to be noted that the statistical significance achieved through
-this method is almost one point higher than that of the BDT method of classification.
+this method is almost one sigma (standar deviation) higher than that of the BDT method of classification.
 
@@
  \item $\Delta \phi$ : the angle between the reconstructed tops.
- \item $cos\theta_{top}$.
+ \item $\cos\theta_{top}$.
 \end{enumerate}
@@
 \begin{equation}
- m_{\tilde{t}}=811\quad \textrm{GeV}/c^{2}
+ m_{\tilde{t}}=811\textrm{GeV}/c^{2}
 \end{equation}
@@
 \begin{equation}
- m_{\tilde{t}}=811\pm 15 \quad \textrm{GeV}
+ m_{\tilde{t}}=811\pm 15 \quad \textrm{GeV/}c^{2}
 \end{equation}
@@
 BDT         &       6.79      &  839 $\pm$ 11 GeV/$c^{2}$      &  493		\\
-GBD         &       7.68      &  811 $\pm$ 15 GeV/$c^{2}$      &  455		\\
+GBDT         &       7.68      &  811 $\pm$ 15 GeV/$c^{2}$      &  455		\\
 \hline
@@
 than those in the GBDT method ($N_{events}$=198), and at first sight it would be expected that the GBDT has 
-better potencial than the BDT.
+better potential than the BDT.
 But the mass and uncertainty measurements proved to be the other way round giving evidence to the fact
@@
 
-Similar contradiccion produces the careful examination of the signal efficiency plots(4.8 for BDT and 4.20
+Similar contradiction produces the careful examination of the signal efficiency plots(4.8 for BDT and 4.20
 for GBDT). Both of them (taking into account the errors) tend to have an almost constant trend but the 
@@
 
-Another interesting fact is the dependence of the discrimination strength of the classifiers with respect to 
+Another interesting observation is the dependence of the discrimination strength of the classifiers with respect to 
 the number of trees. Before I set the number of trees to be 1000, my initial calculation for the mass 
@@
 
-Although, apart from the "tunning" issues, the fact that the BDT's performance is superior is is no 
-new to the experimental world. From 2005, similar studies were made for the MiniBoone experiment and 
+Although, apart from the "tunning" issues, the fact that the BDT's performance is superior is 
+something that the experimental community knew already. 
+From 2005, similar studies were made for the MiniBoone experiment and 
 it was found that BDT's (on Adaboost mode) outperform other methods~\cite{yang2005studies}.
@@
 The mass of the supersymmetric top quark was calculated for the CLIC experiment at $\surd s$ = 3 TeV and for 
-an integrated luminosity $\mathcal{L}_{int}$ = 3000 fb$^{-1}$.
+an integrated luminosity $\mathcal{L}_{int}$ = 3000 fb$^{-1}$ for a nominal mass of $M_{nom}$ = 845 GeV/$c^{2}$.
 
@@
 Althought the GBDT's at first seem to be the best candidate for a more precise mass calculation, the BDT's 
-proved to be the ones that offered a better one. That is because the resulting number of signal events in the BDT 
+proved to be the ones that offered a more precise one. That is because the resulting number of signal events in the BDT 
 method are more than the ones in GBDT implying that having stronger signal than better separation between 
@@
 
+Having in hand the mass of the top squark calculated with the BDT method along with the Monte Carlo mass
+of the neutralino, comparison can be made with figure 3.1 of ATLAS. As it can be seen the set of these masses 
+($m_{\tilde{t}}$ = 839 GeV/$c^{2}$,$m_{\tilde{\chi}_{1}^{0}}$ = 357 GeV/$c^{2}$) belong in the already 
+excluded limits 
+of ATLAS experiment. Besides that, the potencial of CLIC collider for a precise measurement of the mass is 
+not ruled out but on the opposite stressed, given the potencial of low uncertainty on the mass measurement.
+
+Summing up, I demonstrated that it is possible the CLIC experiment to make a precise measurement of the top
+squark mass with significantly low uncertainty for the scenario that the mass of the $\tilde{t}$ is 
+$m_{\tilde{t}}$ = 845 GeV/$c^{2}$ and the mass of the neutralino being $m_{\tilde{\chi}_{1}^{0}}$ = 
+357 GeV/$c^{2}$ investigating the channel:
+
+$e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t \bar{t}\tilde{\chi}_{1}^{0}
+ \tilde{\chi}^{0}_{1} \rightarrow
+ W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0} \rightarrow 
+ q \bar{q} q \bar{q} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}$
+
 \chapter{Further Work}
@@
 \begin{itemize}
- \item As I investigated the following channel
-    \begin{equation}
-      e^{-} e^{+} \rightarrow \tilde{t} \tilde{\bar{t}} \rightarrow t\tilde{\chi}_{1}^{0} \bar{t}\tilde{\chi}_{1}^{0}
-      \rightarrow W^{+}W^{-}b\bar{b} \tilde{\chi}_{1}^{0} \tilde{\chi}_{1}^{0}
-    \end{equation}
-the decay of the W boson can be hadronic or leptonic. By isolating the cases that $W\rightarrow l\nu_{l}$
-,i.e. the hadronic channe, we can possibly achieve even smaller uncertainty in the mass calculation of the top
-squark.
-\item Another possibility is to look also for other decays of the top squarks such as 
+
+\item A possibility is to look also for other decays of the top squarks such as 
     \begin{equation}

### 2017-08-17 Tex_Dissertation/MSc_dissertation.tex
read

@@
 \begin{abstract}
-In this project I calculate the mass of the Supersymmetric top quark in CLIC experiment at $\sqrt{s}$ = 3 TeV
+In this project I measure the mass of the Supersymmetric top quark in CLIC experiment at $\sqrt{s}$ = 3 TeV
 and for an integrated luminosity $\mathcal{L}_{int}$=3000 fb$^{-1}$
-in $e^{-}$ $e^{+}$ collisions. I assume the following decay for the top squark $\tilde{q} \rightarrow q$ 
-$\chi_{0}$, 
-and the final products to be
-$\tilde{q} \rightarrow q$ $\chi_{0} \rightarrow$ $W b \tilde{\chi}_{1}^{0}$ .
-The mass was found  to be  $m_{\tilde{t}}$ = 839 $\pm$ 11 GeV/$c^{2}$ using the Boosted Descision 
+in $e^{-}$ $e^{+}$ collisions. I assume the following decay for the top squark $\tilde{t} \rightarrow t$ $\tilde{\chi}_{1}^{0}$, 
+investigating the channel:
+ $e^{-} e^{+} \rightarrow \tilde{t} \tilde{\bar{t}} \rightarrow t\tilde{\chi}_{1}^{0} \bar{t}\tilde{\chi}_{1}^{0}
+ \rightarrow W^{+}W^{-}b\bar{b} \tilde{\chi}_{1}^{0} \tilde{\chi}_{1}^{0}$. 
+The major background to this signal comes from top quark pair production $e^{-}e^{+}\rightarrow t\bar{t}$
+while other decays of the top squarks were used to model backgrounds from SUSY processes. 
+For a generated Monte Carlo mass $M_{nom}$ = $m_{\tilde{t}}$ = 845 GeV/$c^{2}$, the top squark mass was 
+measured $m_{\tilde{t}}$ = 839 $\pm$ 11 GeV/$c^{2}$ using the Boosted Descision 
 Trees Multivariate Analysis and $m_{\tilde{t}}$ = 861 $\pm$ 15 GeV/$c^{2}$ using the Gradient Boosted Descision  Trees Multivariate Analysis. 
@@
 \begin{itemize}
-
-\item A possibility is to look also for other decays of the top squarks such as 
+ \item As I investigated the following channel
+    \begin{equation}
+      e^{-} e^{+} \rightarrow \tilde{t} \tilde{\bar{t}} \rightarrow t\tilde{\chi}_{1}^{0} \bar{t}\tilde{\chi}_{1}^{0}
+      \rightarrow W^{+}W^{-}b\bar{b} \tilde{\chi}_{1}^{0} \tilde{\chi}_{1}^{0}
+    \end{equation}
+the decay of the W boson can be hadronic or leptonic. By isolating and investigating 
+the cases that $W\rightarrow l\nu_{l}$
+,i.e. the leptonic channel.
+
+\item Another possibility is to look also for other decays of the top squarks such as 
     \begin{equation}
@@
     \end{equation}
+
+\item Besides looking for other decays, work can be done on taking into account on the mass measurement all
+the possible stop decays denoted in page 11. In that case, since there will be no SUSY background work has to
+be done on simulating a new one involving other interactions.
 

### 2017-08-17 Tex_Dissertation/MSc_dissertation.tex
done

@@
 The main targets of CLIC are dependent of the energy stage~\cite{clic2016updated}.
-In the first it will focus on prescision standard model physics such as Higgs and top quark measurements and in the two subsequent, among others, there will be searches
+In the first stage it will focus on prescision standard model physics such as Higgs and top quark measurements and in the two subsequent, among others, there will be searches
 for new physics.
@@
 and a dark matter candidate, the neutralino $\tilde{\chi}_{1}^{0}$. In this project I will use multivariate analysis
-to discriminat between signal and background with the goal to measure the top squark
+to discriminate between signal and background with the goal to measure the top squark
 mass at $\surd{s}$ = 3 TeV in the CLIC accelerator environment.
@@
 At this enegy stage the Higgsstrahlung
-process ($e^{+}e^{-}\rightarrow ZH$) alongside the $WW$ fusion ($e^{+}e^{-}\rightarrow H\nu_{e}\tilde{\nu}_{e}$) 
+process ($e^{+}e^{-}\rightarrow ZH$) alongside the $WW$ fusion ($e^{+}e^{-}\rightarrow H\nu_{e}\bar{\nu}_{e}$) 
 are the dominant and can shed light to properties of the Higgs boson in a model independent way.
@@
 In this chapter I will describe the exact conditions and methods that were followed in this project for the 
-measurement of the stop quark mass at the CLIC Conceptual experiment.
+measurement of the stop quark mass at the CLIC experiment.
 
@@
 
-In this chapter I describe the procedure that I followed until the calculation of the top squark mass. 
+In this chapter I describe the procedure that I followed until the measurement of the top squark mass. 
 This involved vertex finding, jet clustering, flavour tagging and the calculation of the $\chi^{2}$
@@
 Additionally another interesting thing is the importance of these 40 more events in the case of BDT 
-(for the mass and the ancertainty calculation).
+(for the mass and the uncertainty calculation).
 This is clear because in the BDT the number of events of SM background ($N_{events}$=528) 
@@
 that the SM background has reduced significantly. This is the reason why we get a significance of 11 GeV, i.e.
-8 GeV less.
+4 GeV less.
 
 Although, apart from the "tunning" issues, the fact that the BDT's performance is superior is 
-something that the experimental community knew already. 
+something that the experimental community knew. 
 From 2005, similar studies were made for the MiniBoone experiment and 
@@
 of the neutralino, comparison can be made with figure 3.1 of ATLAS. As it can be seen the set of these masses 
-($m_{\tilde{t}}$ = 839 GeV/$c^{2}$,$m_{\tilde{\chi}_{1}^{0}}$ = 357 GeV/$c^{2}$) belong in the already 
+($m_{\tilde{t}}$ = 839 GeV/$c^{2}$, $m_{\tilde{\chi}_{1}^{0}}$ = 357 GeV/$c^{2}$) belong in the already 
 excluded limits 
@@
     \end{equation}
-the decay of the W boson can be hadronic or leptonic. By isolating and investigating 
+the decay of the W boson can be hadronic or leptonic. Isolating and investigating 
 the cases that $W\rightarrow l\nu_{l}$
-,i.e. the leptonic channel.
+,i.e. the leptonic channel a mass measurement can be achieved.
 
@@
 \item Besides looking for other decays, work can be done on taking into account on the mass measurement all
-the possible stop decays denoted in page 11. In that case, since there will be no SUSY background work has to
-be done on simulating a new one involving other interactions.
+the possible stop decays denoted in page 11. In that case, since there will be no SUSY background
+and work has to be done in order to simulate a new one involving other interactions.
 
